### 2015-02-19 IFIP FTA/manuscript.tex
files

\documentclass[10pt]{llncs}

\usepackage{cite}
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage[tight,footnotesize]{subfigure}
\usepackage{graphicx}
\usepackage{url}
\graphicspath{{.}{images/}} % declare the path(s) where your graphic files are
\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{Efficient Representation of Chain Code with Digits of Unequal Cost}
\title{Failure Behaviour Analysis of Automated Pond Oxygen Management System}

\author{Sohag Kabir\inst{1}\and Youcef Gheraibia\inst{2}\and Tanzima Azad\inst{3}}
\institute{Department of Computer Science, University of Hull, Hull, UK\and Department of Computer Science, Badji Mokhtar-Annaba University, Annaba, Algeria\and Department of Computer Science and Engineering, Bangladesh University of Enegineerinag \& Technology, Bangladesh\\
\email{s.kabir@hull.ac.uk, youcef.gheraibia@gmail.com, azad.tanzima@dbbl.com.bd}
}
\maketitle

\begin{abstract}
%\boldmath
Reliability of safety-critical systems are a prime concern of the modern society due to the growing dependence on those systems. Safety of systems is a fundamental requirement for system reliability. Fault tree analysis (FTA) is well-established, powerful, and widely used tool for evaluating system reliability. Fault trees provide a graphical and logical framework for analysing the dependability of systems. They have been successfully employed in studying reliability of a variety of real-world systems. In aquaculture, the volume of oxygen contained in water is considered as a critical parameter for the health and well-being of fishes. If oxygen levels drop below 4 mg/L then fishes may stop feeding, stressed and begin to die. Automated Pond Oxygen Management System is a critical component in aquaculture to maintain the proper oxygen level in water. In summer months, when oxygen level starts dropping due to increased temperature, then Automated Pond Oxygen Management System can balance the oxygen level in water by generating oxygen artificially. Therefore, the failure of this system may result in a disastrous outcome. In this paper, we have used fault tree analysis to evaluate the reliability of a generic automated fault tolerant pond oxygen management system.
\end{abstract}

\section{Introduction}
\label{sec:1}
The increasing complexity of systems has considerable significance for safety analysis as a part of dependability assessment. Dependability assessment of safety-critical
systems should begin early in the design phase so that potential problems can be identified and rectified as soon as possible to avoid expensive changes later in the system life-cycle. If problems are not rectified, system failures can result in unacceptable costs in terms of loss of life, environmental damage, and loss of resources\cite{Bernardi2007}. Most of today's systems have multiple modes of operation and many offer some level of robustness built into the design. Many systems have achieved the capability to operate in a degraded mode without failing completely by adopting some sort of fault-tolerant strategy like using redundant components or using parallel architectures. However, such complexity also poses new challenges for systems analysts, who need to understand how such systems behave and estimate how reliable and safe they really are. System analysis can help reliability engineers understand how systems work and how they can fail, thus allowing them to determine necessary actions to prevent that failure\cite{Martin2009}.

Fault tree analysis (FTA) is well-established and very popular technique for evaluating the safety  and  reliability of complex safety critical systems\cite{Leveson1995}. Fault  trees  utilise  graphical representations  based  on  Boolean  logic  to  show  logical connections  between  different  faults  and  their  causes. They are  a deductive analysis method, which means analysis starts  with  a  system  failure  known  as  the  `top  event'  and works  backwards  to  determine  its  root  causes\cite{Vesely2002}.  From  a  fault tree, it is possible to understand how combinations of failures of  different  components  or  certain  environmental 
circumstances can lead to system failure. Qualitative analysis of  fault tree is performed using Boolean logic by reducing it to minimal cut sets (MCSs) which are the smallest combinations of failure of system components that are necessary and sufficient to cause the system failure. Quantitative  analysis  of  a fault  tree,  which  follows  qualitative  analysis,  can  help  to estimate  the  probability  of  the  top  event  occurring  from  the given failure rates of basic failure modes of the system\cite{Vesely1981}.

Commercial aquaculture is growing worldwide and  according to the Food and Agriculture Organization (FAO), in 2012 aquaculture supplied the world with about 154 million tonnes of fish, of which 131 tonnes was consumed as human food\cite{Fao2012}. Ponds are the most common production systems used globally for fish production. Managing water quality in the pond is one of the most challenging tasks due to their exposure to factors of climate and topography\cite{culberson1996}. Growth rates and survival of the organisms within the pond environment is largely depending on the amount of available oxygen, dissolved oxygen levels and temperatures of pond water\cite{boyd1992, boyd1978}. Specially, in the summer time, when the water temperature goes up, then dissolved oxygen level in the pond water goes down.  Due to this reduced oxygen level fish may stop feeding and begin to die. Fish farmers could prevent oxygen depletion through monitoring and controlling oxygen level by using dissolved oxygen management systems. Therefore the success of oxygen monitoring and controlling process is primarily depends on the successful operation of the oxygen management systems. The failure of this system could lead to a catastrophic outcome. Considering the importance of such a system in fish farming, in this paper, we have performed the reliability analysis of an automated pond oxygen management system.

The paper is organised as follows: Section \ref{sec:2} presents the fundamentals of fault tree analysis. A description of the automated oxygen management system is provided in Section \ref{sec:3}. In Section \ref{sec:4}, the result of the analysis is presented. Finally, concluding remarks are presented in Section \ref{sec:5}.

\section{Fault Tree Analysis}
\label{sec:2}
FTA is the most widely used deductive top down analysis method which allows analysts to perform both qualitative and quantitative analysis\cite{Alain1991, Vesely2002}. Fault trees (FTs) utilise graphical model to show how low-level component failure combines together to cause a top level system failure. FTA starts with an undesired event, such as system failure, known as the `top event', and then works backwards to deduce the causes of the top event in terms of logical combination of basic events\cite{Martin2009}. Symbols used in classical FTs to represent different events are shown in Fig.\ref{fig1}.

A basic event is an initiating or basic fault that does not require any further development or expansion. It is represented as a leaf node in the fault tree. An intermediate event is a fault that is caused by the logical combinations of other events occurring further down the tree. As intermediate events are caused by other events therefore they are almost always a type of logical gate. An undeveloped event is an event whose contributions are not considered in the analysis, either because it is considered as unnecessary, or because insufficient information is available. Normal event does not represent any fault and it is part of the nominal behaviour of the system.  A conditioning event does not necessarily represent a fault, it serves as a special condition or constraint for certain types of gates. Symbols used in classical FTs to represent different logic gates are shown in Fig.\ref{fig2}.  The outcome of OR gate is true if any of the input events are true, whereas an AND gate is true if all of its input events are true. The XOR gate is true if one and only one of its input events is true. The outcome of PAND gate is true if all of its events   are true and they occur in a specific sequence. The INHIBIT gate produce an output when the input event is true in the presence of a conditioning event. Example of a fault tree is shown in Fig.\ref{fig3}\cite{John1998}.

\begin{figure}[thpb]
      \centering
      \framebox{
			\includegraphics[scale=0.70]{events1}%[scale=0.6]
 	  }
      \caption{Fault Tree Event Symbols}
      \label{fig1}
   \end{figure}

\begin{figure}[thpb]
      \centering
      \framebox{
			\includegraphics{gates}%[scale=0.6]
 	  }
      \caption{Fault Tree Logic Gate Symbols}
      \label{fig2}
   \end{figure}

\begin{figure}[thpb]
      \centering

			\includegraphics[scale=0.4]{example_FT1}%[scale=0.6]

      \caption{Example of a Fault Tree}
      \label{fig3}
   \end{figure}

The roles of FTA in decision making are\cite{Vesely2002}:

\begin{itemize}
\item To understand the logic leading to the top event. 
%\item Determination of effective number of iterations for coding with unequal letter cost. 
\item To prioritise the contributors leading to the top event.
\item As a proactive tool to prevent the top event.
\item To monitor the performance of the system.
\item To minimise and optimise resources.
\item To assist the designing of the system.
\item As a diagnostic tool to identify and correct causes of the top event  
\end{itemize}

Steps required for successful FTA and the interrelationship between the steps are shown in Fig.\ref{fig4}\cite{Vesely2002}. The first step is to define the objective of the FTA, i.e., defining the objectives in terms of a failure of the system to be analysed. The top event of the FT is defined in step 2 just after defining the objective of FTA. After that the scope of the FTA is defined by indicating which of the component failures and contributions will be considered and which will not be considered. The level of detail to which the failure causes for the top event will be developed is defined is step 4 as the resolution of FTA. In step 5, ground rules for the FTA are defined by declaring the procedure and nomenclature by which events and gates are named. The ground rules are very important in creating an understandable FT. The actual construction of FT is performed in step 6 and the evaluation is done in Step 7. Both qualitative and quantitative evaluations could be performed. the qualitative evaluation provides information about the minimal cut sets which are necessary and sufficient to cause the top event. The quantitative evaluation usually provides the probability of the top event and importance measure of events based on their contribution to the top event. Quantitative analysis is out of scope of this paper. Finally, at the last step the results are interpreted and presented.   
%\begin{figure}[thpb]
      %\centering
      %\framebox{
			%\includegraphics{block_diagram}%[scale=0.45]
 	  %}
      %\caption{Example of a Fault Tree}
      %\label{fig4}
   %\end{figure}

	\begin{figure}[thpb]
      \centering

			\includegraphics[scale=0.5]{block_diagram1}%[scale=0.45]

      \caption{Fault Tree Analysis Steps}
      \label{fig4}
   \end{figure}	
%%\begin{figure}[thpb]	
%\centerline{\subfigure[Basic event]{\includegraphics{basic_event}
%\label{fig1_a}}
%\hfil
%\subfigure[Intermediate event]{\includegraphics{intermediate_event1}
%\label{fig1_b}}}
%\caption{Classical Fault Tree Event Symbols}
%\label{fig1}
%\end{figure}
      %
%\begin{figure}[thpb]	
%\centerline{\subfigure[OR gate]{\includegraphics{or}
%\label{fig2_a}}
%\hfil
%\subfigure[AND gate]{\includegraphics{and}
%\label{fig2_b}}}
%\caption{Classical Fault Tree Logic Gate Symbols}
%\label{fig2}
%\end{figure}

%\begin{table}[thpb]
%\renewcommand{\arraystretch}{1.3}
%\caption{Fault Tree Symbols}
%\label{table1}
%\centering
%\begin{tabular}{|c|c|c|}
%\hline
 %\textbf{Symbol} & \textbf{Name} & \text{Description}\\
%\hline
%
    %% \raisebox{-\totalheight}
	%\raisebox{-0.7\totalheight}	{\includegraphics{basic_event}} & Basic Event & \begin{tabular}{@{}c@{}}A basic initiating fault requiring no \\ further development\end{tabular}\\
	%\hline
	%\raisebox{-0.7\totalheight}	{\includegraphics{intermediate_event}} & Intermediate Event &\begin{tabular}{@{}c@{}}An event arising from the combination \\ of basic events\end{tabular}\\ 
	%\hline
	%\raisebox{-0.7\totalheight}	{\includegraphics[scale=0.6]{or}} & AND&\begin{tabular}{@{}c@{}}Output fault occurs if all of the input  \\ faults occur\end{tabular} \\ 
	%\hline
	%\raisebox{-0.7\totalheight}	{\includegraphics[scale=0.6]{and}} & OR&\begin{tabular}{@{}c@{}}Output fault occurs if a least one of the  \\ input faults occur\end{tabular} \\  
%\hline
%\end{tabular}
%\end{table}

\section{Automatic Pond Oxygen Management System}
\label{sec:3}
An automated fault-tolerant pond oxygen management system is shown in Fig.\ref{fig5}. The role of this system is to automatically generate oxygen whenever the oxygen level of pond water starts falling. Broadly, this system has a power generation unit and two subsystems (subsystem 1 and 2). The power generation unit consists of an electricity generator and a main electricity supply line. In normal condition, the system is powered by the electricity from the main line. If the main line fails (disconnected or load-shedding) then the generator is enabled to provide electricity to the system. Subsystem 1 and 2 are identical because subsystem 2 is introduced to make the system fault-tolerant. 
%Subsystem 2 is a redundant block and works as a spare component for the system. If subsystem 1 fails then subsystem 2  takes over its tasks. 
Subsystem 1 has an oxygen level sensing block ${OSB}_1$. ${OSB}_1$ block has 2 oxygen dissolver sensor ${OS}_i \left(i=1,2\right)$. Each oxygen dissolver sensor ${OS}_i$ consists of a battery unit and a sensor. For simplicity, the battery unit and the sensor of the oxygen dissolver sensors are not shown in the figure. The oxygen level sensing block ${OSB}_1$ senses the oxygen level of the pond by using oxygen dissolver sensor ${OS}_1$ and sends the reading to the decision making block ${DM}_1 $. If  ${OS}_1$ fails then ${OS}_2$  performs the task of sensing. Therefore, ${OSB}_1$ can still operate if one of its sensors fails. Characteristics and functionality of ${OSB}_2$ are similar to that of ${OSB}_1$. Decision making block can decide whether to turn on an oxygen generator after getting the oxygen level reading from the ${OSB}_1$. If required ${DM}_1$ can turn on an oxygen generator from the oxygen generator block ${OGB}_1$. Failure of ${DM}_1$ would cause the subsystem 1 to fail because there is no spare component to take over its tasks. ${OGB}_1$ block has a dedicated (private) oxygen generator $\left({OG}_1\right)$ and a shared oxygen generator $\left({OG}_3\right)$. In normal condition, ${OG}_1$ is used to generate oxygen. If  ${OG}_1$fails then  ${OGB}_1$ can use ${OG}_3$ to generate oxygen. Similarly, if ${OG}_2$ of ${OGB}_2$ fails then ${OGB}_2$ can use ${OG}_3$ to generate oxygen.

\begin{figure}[thpb]
      \centering

			\includegraphics[scale=0.45]{pond_system1}

      \caption{Automated Fault Tolerant Pond Oxygen Management System}
      \label{fig5}
   \end{figure}

%\begin{figure*}[thpb]
%\centering
%% Use the relevant command for your figure-insertion program
%% to insert the figure file.
%% For example, with the graphicx style use
%\framebox{
			%\includegraphics[scale=0.60]{pond_system}
 	  %}
%\caption{Automated Fault Tolerant Pond Oxygen Management System }
%\label{fig5}       % Give a unique label
%\end{figure*}

\section{ Fault Tree Generation and Evaluation}
\label{sec:4}
Before constructing the FT for the system in Fig.\ref{fig5}, we have defined the objective of the FTA for this system. The objective of the analysis is to find the possible causes that could prohibit the system from generating oxygen when required. To do this we have identified the top event as system failure, i.e. inability of the system to generate oxygen. In this paper, events are assumed to be statistically independent, and to be non-repairable---all common assumptions in FTA. At the same time, we also considered that a component could be either in failed or fully functional state, no other state is possible. The ID and names of the basic events, intermediate events, and top event are shown in Table \ref{table1} and Table \ref{table2} respectively. The fault tree of the system in Fig.\ref{fig5} is shown in Fig.\ref{fig6}.

\begin{table}[thpb]
\renewcommand{\arraystretch}{1.5}
\caption{ID and Name of Basic events}
\label{table1}
\centering
\begin{tabular}{c   c}
\hline
\bfseries Event ID & \bfseries Event Name\\
\hline
MS & Failure of main electricity line\\
%\hline
EG & Failure of electricity Generator\\
%\hline
DM1 & Failure of Decision Maker in subsystem 1\\
%\hline
DM2 & Failure of Decision Maker in subsystem 2\\
%\hline
OG1 & Failure of Oxygen Generator 1 in ${OGB}_1$\\
%\hline
OG2 & Failure of Oxygen Generator 2 in ${OGB}_2$\\
%\hline
OG3 & Failure of Oxygen Generator 3 (shared)\\
%\hline
S1 & Failure of sensor in $OS_1$\\
%\hline
S2 & Failure of sensor in $OS_2$\\
%\hline
S3 & Failure of sensor in $OS_3$\\
%\hline
S4 & Failure of sensor in $OS_4$\\
%\hline
B1 & Failure of battery unit in $OS_1$\\
%\hline
B2 & Failure of battery unit in $OS_2$\\
%\hline
B3 & Failure of battery unit in $OS_3$\\
%\hline
B4 & Failure of battery unit in $OS_4$\\
\hline
\end{tabular}
\end{table}

\begin{table}[thpb]
\renewcommand{\arraystretch}{1.3}
\caption{ID and Name of Intermediate and top events}
\label{table2}
\centering
\begin{tabular}{c c}
\hline
\bfseries Event ID & \bfseries Event Name\\
\hline
TE & System Failure---no oxygen supply\\
%\hline
SSF & Failure of Subsystem 1 and 2\\
%\hline
PS & Failure of Power Supply Block\\
%\hline
SS1 & Failure of Subsystem 1\\
%\hline
SS2 & Failure of Subsystem 2\\
%\hline
OSB1 & Failure of ${OSB}_1$ block\\
%\hline
OSB2 & Failure of ${OSB}_2$ block\\
%\hline
OGB1 & Failure of ${OGB}_1$ block\\
%\hline
OGB2& Failure of ${OGB}_2$ block\\
%\hline
OS1 & Failure of oxygen dissolver $OS_1$ \\
%\hline
OS2 & Failure of oxygen dissolver $OS_2$\\
%\hline
OS3 & Failure of oxygen dissolver $OS_3$\\
%\hline
OS4 & Failure of oxygen dissolver $OS_4$\\
\hline
\end{tabular}
\end{table}

\begin{figure*}[thpb]
\centering
% Use the relevant command for your figure-insertion program
% to insert the figure file.
% For example, with the graphicx style use
\includegraphics[scale=.65]{FTA_main}
\caption{Fault Tree of the System in Fig.\ref{fig5} }
\label{fig6}       % Give a unique label
\end{figure*}

The logical expression of the top event as disjoint sum of minimal cut sets can be given by following expression:

\begin{align*}
\begin{split}
    System~ Failure=MS\cdot EG+S_1S_2S_3S_4+S_1S_2S_3B_4+S_1S_2B_3S_4+S_1S_2B_3B_4~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\+S_1S_2DM_2+S_1S_2OG_2OG_3	+S_1B_2S_3S_4+S_1B_2S_3B_4+S_1B_2B_3S_4~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\+S_1B_2B_3B_4+S_1B_2DM_2+S_1B_2OG_2OG_3+B_1S_2S_3S_4     +B_1S_2S_3B_4~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\+B_1S_2B_3S_4+B_1S_2B_3B_4+B_1S_2DM_2+B_1S_2OG_2OG_3+B_1B_2S_3S_4~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\+B_1B_2S_3B_4		+B_1B_2B_3S_4+B_1B_2B_3B_4+B_1B_2DM_2+B_1B_2OG_2OG_3~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\+DM_1S_3S_4+DM_1S_3B_4+DM_1B_3S_4			+DM_1B_3B_4+DM_1DM_2~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\+DM_1OG_2OG_3+OG_1OG_3S_3S_4+OG_1OG_3S_3B_4+OG_1OG_3B_3S_4~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\+OG_1OG_3B_3B_4+OG_1OG_3DM_2+OG_1OG_2OG_3~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\end{split}  
\end{align*}

From the above expression, we can see that there are 37 minimal cut sets which can cause the system failure. For example, the first cut set $MS\cdot EG$ corresponds to the power generation unit, if both main electricity line and electricity generator fail, then it will cause the power generation unit to fail which will eventually cause the system failure. Because without electricity the system will not be able to operate even though all other components are fully functional. Similarly, the last cut set $OG_1 \cdot OG_2 \cdot OG_3$ represents the scenario when all the oxygen generators fail. In this case, even all other components of the system work properly to detect the oxygen level of the water still the system cannot produce oxygen to balance the oxygen level because none of the oxygen generator is operational to generate oxygen.

\section{Conclusion}
\label{sec:5}
Fault tree analysis is an effective method to evaluate the safety and reliability of safety-critical systems. It has been widely used in the dependability analysis for many complex systems involved in, nuclear reactor, aerospace industry, and chemical plants. This paper demonstrates the use of the FTA for performing reliability analysis of automated pond oxygen management system. We have performed the qualitative analysis to determine the minimal cut sets that are necessary and sufficient to cause the system failure. Our analysis determines 37 different combinations of system component failures that can cause the system failure. The analysis results can be combined to improve the system design, which may lead to a system with higher quality and reliability. At present, as we do not have any quantitative information (e.g. failure rates) about the system components therefore quantitative analysis is not performed. In future, we have the plan to extend this work by collecting quantitative information about the components and performing quantitative analysis of this system.

\bibliographystyle{splncs03}
\bibliography{biblio}
\end{document}

### 2015-02-19 IFIP FTA/manuscript.tex
reltaed work

@@
 
+\textbf{FTA has been widely used in different area in ordre to .....
+US aerospace and missile programs have been proposed a new Methods to perform risk and reliability assessment in the early 1960s [NASA Office].
+FTA an analysis has been used on Clinical work-flows to ensure the safety of these high-risk workflows [lamis].
+The fault tree for pressure tank analysis has been proposed in [NASA Office of Safety and Mission Assurance].
+Elctornics system has used the FTA to study the behaviour of electronics system. Authors in [Microelectronics Reliability] uses FTA on printed circuit board assembly and 
+for assessment of power system reliability [Reliability Engineering  System Safety].
+The industrial systems are the crucial point of failure analysis, software fault tree analysis for product lines has been proposed in  [High Assurance Systems Engineering].
+The biological system uses the FTA to analysis the failure of biomedical operation such as Analysis for Biological Invasions  [Biological Invasions].}
+
 \section{Automatic Pond Oxygen Management System}

### 2015-02-19 IFIP FTA/manuscript.tex
cited

--- 2015-02-19 IFIP FTA/manuscript.tex
@@
 
-\section{Automatic Pond Oxygen Management System}
+FTA has been widely used in different areas to perform both qualitative and quantitative dependability analysis of the systems.
+Systems that have been analysed using FTA include but not limited to propulsion systems on spacecraft, braking systems in cars, Nuclear Power Plants, and so on.
+FTA has been used to analyse the reliability of the power system in  \cite{volkanovski2009}, power supply system to railways in  \cite{Chen2007}, and cogeneration power plant in textile mill in \cite{Ramesh2011}.
+Recently, fault tree analysis has been applied on Clinical workflows to ensure the safety of these high-risk workflows \cite{lamis2014} and it is also used to prevent wrong-side surgery to patients \cite{abecassis2015}.
+\textbf{The fault tree for pressure tank analysis has been proposed in [NASA Office of Safety and Mission Assurance].
+Elctornics system has used the FTA to study the behaviour of electronics system. Authors in [Microelectronics Reliability] uses FTA on printed circuit board assembly and 
+for assessment of power system reliability [Reliability Engineering  System Safety].
+The biological system uses the FTA to analysis the failure of biomedical operation such as Analysis for Biological Invasions  [Biological Invasions].} Different tools like HiP-HOPS\cite{Papadopoulos2012}, Reliability Workbench\cite{Isograph2014}  are available to perform fault tree analysis.
+
+\section{Case Study: Automatic Pond Oxygen Management System}
 \label{sec:3}

### 2015-02-19 IFIP FTA/manuscript.tex
go go gfofofofof

@@
 Systems that have been analysed using FTA include but not limited to propulsion systems on spacecraft, braking systems in cars, Nuclear Power Plants, and so on.
-FTA has been used to analyse the reliability of the power system in  \cite{volkanovski2009}, power supply system to railways in  \cite{Chen2007}, and cogeneration power plant in textile mill in \cite{Ramesh2011}.
+FTA has been used to analyse the reliability of the power system in  \cite{volkanovski2009,cepin2011assessment}, power supply system to railways in  \cite{Chen2007}, and cogeneration power plant in textile mill in \cite{Ramesh2011}.
 Recently, fault tree analysis has been applied on Clinical workflows to ensure the safety of these high-risk workflows \cite{lamis2014} and it is also used to prevent wrong-side surgery to patients \cite{abecassis2015}.
 \textbf{The fault tree for pressure tank analysis has been proposed in [NASA Office of Safety and Mission Assurance].
-Elctornics system has used the FTA to study the behaviour of electronics system. Authors in [Microelectronics Reliability] uses FTA on printed circuit board assembly and 
+Elctornics system has used the FTA to study the behaviour of electronics system. Authors in \cite{shu2006using} uses FTA on printed circuit board assembly and 
 for assessment of power system reliability [Reliability Engineering  System Safety].
-The biological system uses the FTA to analysis the failure of biomedical operation such as Analysis for Biological Invasions  [Biological Invasions].} Different tools like HiP-HOPS\cite{Papadopoulos2012}, Reliability Workbench\cite{Isograph2014}  are available to perform fault tree analysis.
+The biological system uses the FTA to analysis the failure of biomedical operation such as Analysis for Biological Invasions  \cite{hayes2002identifying}.} Different tools like HiP-HOPS\cite{Papadopoulos2012}, Reliability Workbench\cite{Isograph2014}  are available to perform fault tree analysis.
 

### 2015-02-19 Switche Paper 1st approache/elsarticle-template-num.tex
go go gfofofofof

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{algcompatible}

%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Nuclear Physics B}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Reducing Power Consumption in Huffman Coding}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{}

\address{}

\begin{abstract}
%% Text of abstract

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
\section{Background}
\subsection{Huffman Coding}
\subsection{Power consumption}
\subsection{Issues in Biological data transmission}
\section{GA-SO : Genetic algorithm for Switches Optimising}
Genetic algorithm (GA) is one the of the most popular bio-inspired meta-heuristic algorithm inspired from the natural evolution of species []. It is a  population based algorithm starts with the generation of a random initial population. The population contain a set of feasible solutions called individuals, that are usually far from the optimal. The GA optimisation process uses a set of natural genetic operators such as selection, crossover and mutation to converge to the optimal solution.
\subsection{Preparing data and population generation}
Huffman algorithm read the whole message to compute frequencies. The proposed algorithm read the whole genome to generate the frequencies of the triplet and by the way to generate the adjacent matrix which represents the frequencies precedence of between triplet. The initial population is generated randomly, each solution on the population represents a tree that generates a set of codes equal to the total triplets number.
\subsection{Selection}
The first operator of the genetic algorithm is the selection []. The main objective of the selection is to choose the part of the current  population to be a candidate for the different genetic operators in order to breed the next generation population. Many selection techniques have been proposed in the literature []. In this approach the  process of natural selection is maintained. First we generate a random pair numbers \textit{$rand$} between 2 and the population size, this number represent how many parents will be processed. After that, an unbiased random selection of \textit{$rand$}~individuals (solutions) from the population is maid. 
\subsection{Crossover}
The main operator of the GA is the crossover, allows to construct new solutions from the selected part of the population. The selected solutions are ranked by fitness and crossover two by two from high fitness to low. The main objective of the crossover is to benefits from the two good solutions in order to generate a better solution. An internal node for each tree (solution) is selected (\textit{$node1$},\textit{$node2$}), these two nodes must have the same number of leaf nodes (contain the same number of codes). The crossover operation will create two new trees (solutions), the first child (second) contain the nodes that are not children of the \textit{$node1$} (\textit{$node2$}) and we replace the children of \textit{$node1$} (\textit{$node2$}) by the children of \textit{$node2$} (\textit{$node1$}) (see fig.1). 
\subsection{Mutation}
The mutation operator changes the positions of two leaf nodes of the generated children (result of the crossover); this introduce the diversity in the search process, this diversification strategy allow the algorithm do conference to the global optimum. The algorithm for this operator goes through the leaf nodes and change the position of two leaf nodes from a parent to another and selects the ones to change according to a fixed mutation rate (see fig.1).
\subsection{Population update}
The crossover operation aims to generate new solutions from the current solution to built the second generation of the population. Furthermore, the mutation provide the diversity on the search space solution by changing the position of  nodes on the same tree. After these two operations, the next step of the genetic algorithm is two to breed the new population. Firstly the new solutions (children) are added to the current population, after that the population is ranked by fitness. The algorithm remove the worst solutions until the initial size of the population is achieved. The algorithm genetic repeat these operators until the stopped criteria is achieved, in this algorithm the stopped criteria is when the objective function (number of switches) stop decreasing.
\begin{algorithm}[!btph]
\caption{Switches optimising Huffman codes}
\label{alg1}
\begin{algorithmic}[1]
\REQUIRE Textual representation of a Genome
\ENSURE Low switches Huffman codes
\STATE Generate triplet frequencies and adjacent matrix 
\STATE Generate the initial  population of trees
\REPEAT 
\STATE Select part of the population
\STATE Generate children candidates via crossover
\STATE Mutate children
\STATE Add children to population
\STATE Rank by fitness
\STATE Remove worst solutions until population limit
\UNTIL{The switches number stop decreasing}
%\algstore{myalg}
\end{algorithmic}
\end{algorithm}
\begin{figure}[t]
\begin{center}
\includegraphics[width=400pt,height=545pt]{Images/Drawing1-1.jpg}
\caption{The Crossover operator}
\end{center}
\label{Fig1}
\end{figure}
\begin{figure}[h]
\begin{center}
\includegraphics[width=200pt,height=200pt]{Images/Drawing2.jpg}
\caption{The Mutation operator}
\end{center}
\label{Fig1}
\end{figure}
\section{Experiments and Comparison}
\subsection{Datasets Description}
\subsection{Results}
\begin{table}[h]
\renewcommand{\arraystretch}{1.1}
\small
\label{table4}
\caption{Comparison of performance among classical Huffman code, CCA, and OCCA without penalty}
%\begin{center}

\begin{tabular}{c  c c  c c  c c}
\hline
 & Huffman Algorithm & P \\\hline
\\\hline
Genome 1& 18.16 & 10.05 & 44.65 \\\hline
Genome 2& 24.66 &  15.63 & 36.61 \\\hline
Genome 3&18.46 &  10.66&  42.25\\\hline
Genome 4&25.18&16.26& 35.42\\\hline
Genome 5& 19.24& 16.08 & \\\hline
Genome 6& &\\\hline
Genome 7& &\\\hline
Genome 8& & \\\hline
Genome 9& &\\\hline
Genome 10& & \\\hline
Genome 11& & \\\hline
Genome 12& &\\\hline
Genome 13& &\\\hline
Genome 14& & \\\hline
Genome 15& & \\\hline
Genome 16&& \\\hline
Genome 17& & \\\hline
Genome 18& & \\\hline

%\bottomrule
\end{tabular}
%\end{center}
\end{table}
\section{Conclusion}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-num} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\begin{thebibliography}{00}

%% \bibitem{label}
%% Text of bibliographic item

\bibitem{}

\end{thebibliography}
\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2015-02-19 IFIP FTA/manuscript.tex
some edit

@@
 \author{Sohag Kabir\inst{1}\and Youcef Gheraibia\inst{2}\and Tanzima Azad\inst{3}}
-\institute{Department of Computer Science, University of Hull, Hull, UK\and Department of Computer Science, Badji Mokhtar-Annaba University, Annaba, Algeria\and Department of Computer Science and Engineering, Bangladesh University of Enegineerinag \& Technology, Bangladesh\\
-\email{s.kabir@hull.ac.uk, youcef.gheraibia@gmail.com, azad.tanzima@dbbl.com.bd}
+\institute{Department of Computer Science, University of Hull, Hull, UK\and Department of Computer Science and Mathematics,  Mohamed-Cherif Messaadia University, Souk Ahras, Algeria\and Department of Computer Science and Engineering, Bangladesh University of Enegineerinag \& Technology, Dhaka, Bangladesh\\
+\email{s.kabir@hull.ac.uk, youcef.gheraibia@univ-soukahras.dz, azad.tanzima@dbbl.com.bd}
 }
@@
 %\boldmath
-Reliability of safety-critical systems are a prime concern of the modern society due to the growing dependence on those systems.
+Dependability of safety-critical systems is a prime concern of the modern society due to the growing dependence on those systems.
 Safety of systems is a fundamental requirement for system reliability.
-Fault tree analysis (FTA) is well-established, powerful, and widely used tool for evaluating system reliability.
+Fault tree analysis (FTA) is well-established, powerful, and widely used tool for evaluating system safety.
 Fault trees provide a graphical and logical framework for analysing the dependability of systems.
-They have been successfully employed in studying reliability of a variety of real-world systems.
+They have been successfully employed in studying failure behaviour of a variety of real-world systems.
 In aquaculture, the volume of oxygen contained in water is considered as a critical parameter for the health and well-being of fishes.
 If oxygen levels drop below 4 mg/L then fishes may stop feeding, stressed and begin to die.
-Automated Pond Oxygen Management System is a critical component in aquaculture to maintain the proper oxygen level in water.
-In summer months, when oxygen level starts dropping due to increased temperature, then Automated Pond Oxygen Management System can balance the oxygen level in water by generating oxygen artificially.
+Automated Pond Oxygen Management System (APOMS) is a critical component in aquaculture to maintain the proper oxygen level in water.
+In summer months, when oxygen level starts dropping due to increased temperature, then the APOMS can balance the oxygen level in water by generating oxygen artificially.
 Therefore, the failure of this system may result in a disastrous outcome.
@@
 Systems that have been analysed using FTA include but not limited to propulsion systems on spacecraft, braking systems in cars, Nuclear Power Plants, and so on.
+Different tools like HiP-HOPS\cite{Papadopoulos2012}, Reliability Workbench\cite{Isograph2014}  are available to perform fault tree analysis.
 FTA has been used to analyse the reliability of the power system in  \cite{volkanovski2009,cepin2011assessment}, power supply system to railways in  \cite{Chen2007}, and cogeneration power plant in textile mill in \cite{Ramesh2011}.
 Recently, fault tree analysis has been applied on Clinical workflows to ensure the safety of these high-risk workflows \cite{lamis2014} and it is also used to prevent wrong-side surgery to patients \cite{abecassis2015}.
-\textbf{The fault tree for pressure tank analysis has been proposed in [NASA Office of Safety and Mission Assurance].
-Elctornics system has used the FTA to study the behaviour of electronics system. Authors in \cite{shu2006using} uses FTA on printed circuit board assembly and 
-for assessment of power system reliability [Reliability Engineering  System Safety].
-The biological system uses the FTA to analysis the failure of biomedical operation such as Analysis for Biological Invasions  \cite{hayes2002identifying}.} Different tools like HiP-HOPS\cite{Papadopoulos2012}, Reliability Workbench\cite{Isograph2014}  are available to perform fault tree analysis.
+Authors in \cite{shu2006using} uses FTA to analyse the potential failure scenarios in the assembly process of the printed circuit board industries.
+In the biological domain, FTA is used to analyse the failure of biomedical operation such as analysis for biological invasions  \cite{hayes2002identifying}.
 

### 2015-02-20 IFIP FTA/manuscript.tex
finished

@@
 %\title{Efficient Representation of Chain Code with Digits of Unequal Cost}
-\title{Failure Behaviour Analysis of Automated Pond Oxygen Management System}
+\title{Failure Behaviour Analysis of Automated Pond Oxygen Management System: a Qualitative Study}
 
-\author{Sohag Kabir\inst{1}\and Youcef Gheraibia\inst{2}\and Tanzima Azad\inst{3}}
+\author{Sohag Kabir\inst{1}\and Youcef Gheraibia\inst{2} \and Martin Walker\inst{1}\and Tanzima Azad\inst{3}}
 \institute{Department of Computer Science, University of Hull, Hull, UK\and Department of Computer Science and Mathematics,  Mohamed-Cherif Messaadia University, Souk Ahras, Algeria\and Department of Computer Science and Engineering, Bangladesh University of Enegineerinag \& Technology, Dhaka, Bangladesh\\
-\email{s.kabir@hull.ac.uk, youcef.gheraibia@univ-soukahras.dz, azad.tanzima@dbbl.com.bd}
+\email{s.kabir@hull.ac.uk, youcef.gheraibia@univ-soukahras.dz, Martin.Walker@hull.ac.uk, azad.tanzima@dbbl.com.bd}
 }
@@
 %\boldmath
-Dependability of safety-critical systems is a prime concern of the modern society due to the growing dependence on those systems.
+Dependability of safety-critical systems are a prime concern of the modern society due to the growing dependence on those systems.
 Safety of systems is a fundamental requirement for system reliability.
-Fault tree analysis (FTA) is well-established, powerful, and widely used tool for evaluating system safety.
+Fault tree analysis (FTA) is powerful, well-established,  and widely used tool for evaluating system safety.
 Fault trees provide a graphical and logical framework for analysing the dependability of systems.
-They have been successfully employed in studying failure behaviour of a variety of real-world systems.
+They have been successfully employed in studying the failure behaviour of a variety of real-world systems.
 In aquaculture, the volume of oxygen contained in water is considered as a critical parameter for the health and well-being of fishes.
@@
 Therefore, the failure of this system may result in a disastrous outcome.
-In this paper, we have used fault tree analysis to evaluate the reliability of a generic automated fault tolerant pond oxygen management system.
+In this paper, we have used fault tree analysis to determine the failure behaviour of an automated fault tolerant pond oxygen management system.
 \end{abstract}
@@
 
-Commercial aquaculture is growing worldwide and  according to the Food and Agriculture Organization (FAO), in 2012 aquaculture supplied the world with about 154 million tonnes of fish, of which 131 tonnes was consumed as human food\cite{Fao2012}.
+Commercial aquaculture is growing worldwide and  according to the Food and Agriculture Organization (FAO), in 2012 aquaculture supplied the world with about 154 million tonnes of fish, of which 131 tonnes were consumed as human food\cite{Fao2012}.
 Ponds are the most common production systems used globally for fish production.
 Managing water quality in the pond is one of the most challenging tasks due to their exposure to factors of climate and topography\cite{culberson1996}.
-Growth rates and survival of the organisms within the pond environment is largely depending on the amount of available oxygen, dissolved oxygen levels and temperatures of pond water\cite{boyd1992, boyd1978}.
+Growth rates and survival of the organisms within the pond environment is largely depending on the amount of available oxygen, dissolved oxygen levels and temperatures of pond water\cite{boyd2002, boyd1978}.
 Specially, in the summer time, when the water temperature goes up, then dissolved oxygen level in the pond water goes down.
-Due to this reduced oxygen level fish may stop feeding and begin to die.
+Due to this reduced oxygen level, fish may stop feeding and begin to die.
 Fish farmers could prevent oxygen depletion through monitoring and controlling oxygen level by using dissolved oxygen management systems.
@@
 The failure of this system could lead to a catastrophic outcome.
-Considering the importance of such a system in fish farming, in this paper, we have performed the reliability analysis of an automated pond oxygen management system.
+Considering the importance of such a system in fish farming, in this paper, we have performed the failure behaviour analysis of an automated pond oxygen management system.
 
@@
 In Section \ref{sec:4}, the result of the analysis is presented.
-Finally, concluding remarks are presented in Section \ref{sec:5}.
+Finally, concluding remarks is presented in Section \ref{sec:5}.
 
@@
 \label{sec:2}
-FTA is the most widely used deductive top down analysis method which allows analysts to perform both qualitative and quantitative analysis\cite{Alain1991, Vesely2002}.
+FTA is the most widely used deductive, top down analysis method which allows analysts to perform both qualitative and quantitative analysis\cite{Alain1991, Vesely2002}.
 Fault trees (FTs) utilise graphical model to show how low-level component failure combines together to cause a top level system failure.
@@
 The INHIBIT gate produce an output when the input event is true in the presence of a conditioning event.
-Example of a fault tree is shown in Fig.\ref{fig3}\cite{John1998}.
+Example of a fault tree is shown in Fig.\ref{fig3}.
 
@@
       \framebox{
-			\includegraphics[scale=0.70]{events1}%[scale=0.6]
+			\includegraphics[scale=0.60]{events1}%[scale=0.6]
  	  }
@@
       \framebox{
-			\includegraphics{gates}%[scale=0.6]
+			\includegraphics[scale=0.64]{gates1}%[scale=0.6]
  	  }
@@
 
-			\includegraphics[scale=0.4]{example_FT1}%[scale=0.6]
+			\includegraphics[scale=0.5]{example_FT1}%[scale=0.6]
 
-      \caption{Example of a Fault Tree}
+      \caption{Example of a Fault Tree\cite{John1998}}
       \label{fig3}
@@
 
-Steps required for successful FTA and the interrelationship between the steps are shown in Fig.\ref{fig4}\cite{Vesely2002}.
+Steps required for successful FTA and the interrelationship between the steps are shown in Fig.\ref{fig4}.
 The first step is to define the objective of the FTA, i.e., defining the objectives in terms of a failure of the system to be analysed.
@@
 The actual construction of FT is performed in step 6 and the evaluation is done in Step 7.
-Both qualitative and quantitative evaluations could be performed.
-the qualitative evaluation provides information about the minimal cut sets which are necessary and sufficient to cause the top event.
+Both qualitative and quantitative evaluations of system failure behaviour could be performed using FTA.
+The qualitative evaluation provides information about the minimal cut sets which are necessary and sufficient to cause the top event.
 The quantitative evaluation usually provides the probability of the top event and importance measure of events based on their contribution to the top event.
@@
 
-      \caption{Fault Tree Analysis Steps}
+      \caption{Fault Tree Analysis Steps\cite{Vesely2002}}
       \label{fig4}
@@
 FTA has been widely used in different areas to perform both qualitative and quantitative dependability analysis of the systems.
-Systems that have been analysed using FTA include but not limited to propulsion systems on spacecraft, braking systems in cars, Nuclear Power Plants, and so on.
+Systems that have been analysed using FTA include but not limited to propulsion systems on spacecraft, braking systems in cars, nuclear power plants, and so on.
 Different tools like HiP-HOPS\cite{Papadopoulos2012}, Reliability Workbench\cite{Isograph2014}  are available to perform fault tree analysis.
 FTA has been used to analyse the reliability of the power system in  \cite{volkanovski2009,cepin2011assessment}, power supply system to railways in  \cite{Chen2007}, and cogeneration power plant in textile mill in \cite{Ramesh2011}.
-Recently, fault tree analysis has been applied on Clinical workflows to ensure the safety of these high-risk workflows \cite{lamis2014} and it is also used to prevent wrong-side surgery to patients \cite{abecassis2015}.
+Recently, fault tree analysis has been applied on clinical workflows to ensure the safety of these high-risk workflows \cite{lamis2014} and it is also used to prevent wrong-side surgery to patients \cite{abecassis2015}.
 Authors in \cite{shu2006using} uses FTA to analyse the potential failure scenarios in the assembly process of the printed circuit board industries.
@@
 \label{sec:3}
-An automated fault-tolerant pond oxygen management system is shown in Fig.\ref{fig5}.
+An automated, fault-tolerant pond oxygen management system is shown in Fig.\ref{fig5}.
 The role of this system is to automatically generate oxygen whenever the oxygen level of pond water starts falling.
@@
 The oxygen level sensing block ${OSB}_1$ senses the oxygen level of the pond by using oxygen dissolver sensor ${OS}_1$ and sends the reading to the decision making block ${DM}_1 $.
-If  ${OS}_1$ fails then ${OS}_2$  performs the task of sensing.
+If  ${OS}_1$ fails, then ${OS}_2$  performs the task of sensing.
 Therefore, ${OSB}_1$ can still operate if one of its sensors fails.
@@
 If  ${OG}_1$fails then  ${OGB}_1$ can use ${OG}_3$ to generate oxygen.
-Similarly, if ${OG}_2$ of ${OGB}_2$ fails then ${OGB}_2$ can use ${OG}_3$ to generate oxygen.
+Similarly, if ${OG}_2$ of ${OGB}_2$ fails, then ${OGB}_2$ can use ${OG}_3$ to generate oxygen.
 
@@
 The objective of the analysis is to find the possible causes that could prohibit the system from generating oxygen when required.
-To do this we have identified the top event as system failure, i.e.
-inability of the system to generate oxygen.
+To do this we have identified the inability of the system to generate oxygen as the top event  (system failure).
 In this paper, events are assumed to be statistically independent, and to be non-repairable---all common assumptions in FTA.
 At the same time, we also considered that a component could be either in failed or fully functional state, no other state is possible.
+The fault tree creation process starts with the top event, represented as the disjunction of the causes of the top event.
+In each iteration, the process propagates downwards to find the causes of system failure from the system level to the subsystem level, and it continues till the propagation reaches to the basic component level.
+In other words, we can say that in each iteration the fault tree expands and grows downwards.
+For example, at the higher level, the system failure can be caused by the failure of the power supply block (PS) or the failure of both the subsystems (SSF).
+The power supply block itself will be failed if and only if the main supply line and the electricity generator fails.
+The fault tree of the system of Fig.\ref{fig5} is shown in Fig.\ref{fig6}.
 The ID and names of the basic events, intermediate events, and top event are shown in Table \ref{table1} and Table \ref{table2} respectively.
-The fault tree of the system in Fig.\ref{fig5} is shown in Fig.\ref{fig6}.
 
@@
 
-\begin{figure*}[thpb]
+\begin{figure}[thpb]
 \centering
@@
 % For example, with the graphicx style use
-\includegraphics[scale=.65]{FTA_main}
+\includegraphics[scale=.40]{FTA_main}
 \caption{Fault Tree of the System in Fig.\ref{fig5} }
 \label{fig6}       % Give a unique label
-\end{figure*}
+\end{figure}
 
-The logical expression of the top event as disjoint sum of minimal cut sets can be given by following expression:
+The logical expression of the top event as the disjoint sum of minimal cut sets can be given by following expression:
 
@@
 In this case, even all other components of the system work properly to detect the oxygen level of the water still the system cannot produce oxygen to balance the oxygen level because none of the oxygen generator is operational to generate oxygen.
+All other cut sets can be interpreted in the similar way.
+The results produced by the FTA provide useful information about the root causes of the system failure, which help the analysts to understand the failure behaviour of the system.
+Now, if required, the analysts can decide to change the system model based on the failure behaviour of the system to satisfy their safety requirements.
+More information about the reliability of the system can be generated through quantitative analysis.
+At present, the quantitative analysis of the system is not performed due to the unavailability of sufficient numerical data for the components of the system.
 
@@
 It has been widely used in the dependability analysis for many complex systems involved in, nuclear reactor, aerospace industry, and chemical plants.
-This paper demonstrates the use of the FTA for performing reliability analysis of automated pond oxygen management system.
+This paper demonstrates the use of the FTA for performing failure behaviour analysis of automated pond oxygen management system.
 We have performed the qualitative analysis to determine the minimal cut sets that are necessary and sufficient to cause the system failure.
@@
 The analysis results can be combined to improve the system design, which may lead to a system with higher quality and reliability.
-At present, as we do not have any quantitative information (e.g.
-failure rates) about the system components therefore quantitative analysis is not performed.
-In future, we have the plan to extend this work by collecting quantitative information about the components and performing quantitative analysis of this system.
+At present, as we do not have sufficient quantitative information (e.g., failure rates) about the system components therefore quantitative analysis is not performed.
+In the future, we have a plan to extend this work by collecting quantitative information about the components and performing quantitative analysis of this system.
 

### 2015-02-20 IFIP FTA/manuscript.tex
done

@@
 %\title{Efficient Representation of Chain Code with Digits of Unequal Cost}
-\title{Failure Behaviour Analysis of Automated Pond Oxygen Management System: a Qualitative Study}
+\title{Failure Behaviour Analysis of Automated Pond Oxygen Management System: A Qualitative Study}
 
 \author{Sohag Kabir\inst{1}\and Youcef Gheraibia\inst{2} \and Martin Walker\inst{1}\and Tanzima Azad\inst{3}}
-\institute{Department of Computer Science, University of Hull, Hull, UK\and Department of Computer Science and Mathematics,  Mohamed-Cherif Messaadia University, Souk Ahras, Algeria\and Department of Computer Science and Engineering, Bangladesh University of Enegineerinag \& Technology, Dhaka, Bangladesh\\
+\institute{Department of Computer Science, University of Hull, Hull, UK\and Department of Computer Science and Mathematics,  Mohamed-Cherif Messaadia University, Souk Ahras, Algeria\and Department of Computer Science and Engineering, Bangladesh University of Engineering \& Technology, Dhaka, Bangladesh\\
 \email{s.kabir@hull.ac.uk, youcef.gheraibia@univ-soukahras.dz, Martin.Walker@hull.ac.uk, azad.tanzima@dbbl.com.bd}

### 2015-02-20 Switche Paper 1st approache/elsarticle-template-num.tex
good

@@
 Genome 4&25.18&16.26& 35.42\\\hline
-Genome 5& 19.24& 16.08 & \\\hline
-Genome 6& &\\\hline
-Genome 7& &\\\hline
-Genome 8& & \\\hline
+Genome 5& 19.24& 16.08 &16.42 \\\hline
+Genome 6& 19.61&14.96&23.71\\\hline
+Genome 7& 22.40 &13.21&41.02\\\hline
+Genome 8&23.87 & \\\hline
 Genome 9& &\\\hline

### 2015-02-20 Switche Paper 1st approache/elsarticle-template-num.tex
switches paper

--- 2015-02-19 Switche Paper 1st approache/elsarticle-template-num.tex
@@
 \usepackage{amssymb}
+\usepackage{booktabs}
 \usepackage{algorithm}
@@
 \usepackage{algcompatible}
-
+\usepackage{multirow}
 %% The amsthm package provides extended theorem environments
@@
 \subsection{Issues in Biological data transmission}
+The size of biological data base increase with an expanding rate and it doesn't stop for increasing.
+In the last decade the use of biological data history increase which evolve a high request to data from this high volume biological data base.
+The exponential growth of these databases become a big problem to all biological data processing methods.
+Data compression methods is the most used methods to evolve the reduce the cost of treatment of high volume data bases.
+The main objective of data compression methods is minimising the number of bits in the data representation.
+Authors in [] proposed a new approach to genomic data compression based in suffix and common substring and code the difference with Huffman code.
+In [16], authors propose a general scheme for coding only the difference between the target genome and the referential one, the coding method used is Huffman.
+Recent work on data compression for biological data have been proposed to deal with transmission of genomic data as an email attachment [][][].
+Cost of data transmission is based on two point, firstly the size of the data which has been improved considerably in the recent year with the improvement of Huffman code.
+Secondly, is the number of switches on the generated codes.
+The power consumption increase linear with the number of switches.
 \section{GA-SO : Genetic algorithm for Switches Optimising}
@@
 \end{algorithm}
-\begin{figure}[t]
+\begin{figure}[tbph]
 \begin{center}
@@
 \end{figure}
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=200pt,height=200pt]{Images/Drawing2.jpg}
-\caption{The Mutation operator}
-\end{center}
-\label{Fig1}
-\end{figure}
+
 \section{Experiments and Comparison}
-\subsection{Datasets Description}
-\subsection{Results}
+
+The effectiveness of the approach has been evaluated with different real genomic biological data, these genomes were downloaded from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$ \cite{pruitt2009ncbi}.
+We focused on the sequences alone, ignoring any header and any other exogenous information.
+In table 3, the different data sets are described with the size  of each of them in megabytes (MB) and the references on the biological data bank.
+
+\begin{table}[!thpb]
+
+\small
+\label{table3}
+\caption{Datasets description}
+%\begin{center}
+\centering
+\begin{tabular}{c  c  c c}
+\toprule
+$\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size (MB)}$ &	$\textbf{Reference}$ \\\hline
+Genome 1& Mycobacterium smegmatis &  6.66 & CP009496  \\\hline
+
+Genome 2& Amycolatopsis benzoatilytica & 8.30 & NZ\_KB912942 \\\hline
+
+\multirow{2}{*}{Genome 3}&Mycobacterium rhodesiae& \multirow{2}{*}{6.11} & \multirow{2} {*}{CP003169}\\ 
+&NBB3& &\\
+\hline
+
+\multirow{2}{*}{Genome 4 }&Streptomyces bottropensis& \multirow{2}{*}{8.54} &
+\multirow{2}{*}{NZ\_KB911581} \\ 
+& ATCC 25435 \\
+\hline
+
+\multirow{2}{*}{Genome 5}&Mycobacterium smegmatis& \multirow{2}{*}{ 6.66} &\multirow{2}{*}{CP009494             } \\ 
+&str. MC2 155 \\
+\hline
+
+\multirow{2}{*}{Genome 6}&Mycobacterium smegmatis& \multirow{2}{*}{6.76} &\multirow{2}{*}{NZ\_KI421511}\\   &MKD8& &\\
+\hline
+
+Genome 7& Bradyrhizobium WSM471&  7.42 &NZ\_CM001442\\\hline
+
+\multirow{2}{*}{Genome 8}&Amycolatopsis thermoflava&  \multirow{2}{*}{8.27} &\multirow{2}{*}{NZ\_CM001442}\\   &N1165 & \\
+\hline
+
+\multirow{2}{*}{Genome 9}&Bacillus thuringiensis&   \multirow{2}{*}{5.74} &\multirow{2}{*}{ NZ\_CM000747 }\\    &Bt407&\\
+\hline
+
+\multirow{2}{*}{Genome 10}&Bacillus thuringiensis& \multirow{2}{*}{6.03} &\multirow{2}{*}{ NZ\_CM000748}\\    &serovar thuringiensis& \\
+\hline
+
+\multirow{2}{*}{Genome 11}&Pseudomonas aeruginosa& \multirow{2}{*}{6.48} &\multirow{2}{*}{NZ\_AFXI01000001}\\    &9BR&\\
+\hline
+
+\multirow{2}{*}{Genome 12}&Bacillus thuringiensis&  \multirow{2}{*}{5.97} &\multirow{2}{*}{ NZ\_CM000753}\\    &serovar berliner ATCC &\\
+\hline
+
+\multirow{2}{*}{Genome 13}&Bacillus thuringiensis& \multirow{2}{*}{5.75} &\multirow{2}{*}{ NZ\_CM000750 }\\    &serovar pakistani&\\
+\hline
+
+\multirow{2}{*}{Genome 14}&Pseudomonas aeruginosa& \multirow{2}{*}{6.28} &\multirow{2}{*}{CP006982}\\    &LES400&\\
+\hline
+
+\multirow{2}{*}{Genome 15}& Mus musculus & \multirow{2}{*}{25.58} &\multirow{2}{*}{GL456087}\\  &chromosome 1&\\
+\hline
+
+\multirow{2}{*}{Genome 16}& Danio rerio & \multirow{2}{*}{56.14} &\multirow{2}{*}{CM002885}\\ & chromosome 1 &\\
+\hline
+\multirow{2}{*}{Genome 17}&Homo sapiens & \multirow{2}{*}{76.64 } &\multirow{2}{*}{  CM000680  }\\    & chromosome 18 &\\
+\hline
+\multirow{2}{*}{Genome 18}&Homo sapiens & \multirow{2}{*}{99.94} &\multirow{2}{*}{CM000684   }\\ & chromosome 22&\\
+\hline
+%\bottomrule
+\end{tabular}
+%\end{center}
+\end{table}
+
 \begin{table}[h]
@@
 Genome 4&25.18&16.26& 35.42\\\hline
-Genome 5& 19.24& 16.08 & \\\hline
-Genome 6& &\\\hline
-Genome 7& &\\\hline
-Genome 8& & \\\hline
-Genome 9& &\\\hline
-Genome 10& & \\\hline
-Genome 11& & \\\hline
-Genome 12& &\\\hline
-Genome 13& &\\\hline
-Genome 14& & \\\hline
-Genome 15& & \\\hline
-Genome 16&& \\\hline
-Genome 17& & \\\hline
-Genome 18& & \\\hline
+Genome 5& 19.24& 16.08 &16.42 \\\hline
+Genome 6& 19.61&14.96&23.71\\\hline
+Genome 7& 22.40 &13.21&41.02\\\hline
+Genome 8&23.87 & 17.70 &25.84\\\hline
+Genome 9&17.66 &10.04&43.14\\\hline
+Genome 10& 18.14 &9.89& 45.47 \\\hline
+Genome 11&19.63&11.48&41.51 \\\hline
+Genome 12& 17.59&11.86&32.57 \\\hline
+Genome 13& &&\\\hline
+Genome 14& && \\\hline
+Genome 15& && \\\hline
+Genome 16&&& \\\hline
+Genome 17& && \\\hline
+Genome 18& && \\\hline
 

### 2015-02-22 Switche Paper 1st approache/elsarticle-template-num.tex
intro

@@
 \section{Introduction}
+In the recent years, application of battery-powered portable devices, e.g.
+laptop computers, personal digital assistant (PDA),  and mobile phones has increased significantly.
+The reliability and performance of such devices are primarily dependent  on their power consumption, e.g., effective battery life.
+Bigger battery size could help to improve power efficiency, however, in a portable device the size of the battery is restricted by the size and weight of the device itself.
+The cost of providing power both in portable and non-portable devices has resulted in significant interest in power reduction.
+CMOS technologies were developed in order to reduce the power consumption both in data processing and transmission.
+In \cite{chandrakasan1995}, an approach was proposed to minimise power consumption in CMOS circuits.
+The method considers optimising the technology used to implement the digital circuits, circuits style and topology, the architecture for implementing the circuits and the algorithms that are being implemented in the devices.
+
 \section{Background}
@@
 
-\begin{thebibliography}{00}
-
-%% \bibitem{label}
-%% Text of bibliographic item
-
-\bibitem{}
-
-\end{thebibliography}
+\section*{References}
+\bibliographystyle{elsarticle-num}
+\bibliography{mybib}
 \end{document}

### 2015-02-22 Switche Paper 1st approache/elsarticle-template-num.tex
intro

@@
 
+As data transmission is a common operation in both portable and non-portable devices, therefore, reducing power dissipation in transmission systems is important.
+Authors in \cite{Gregori2004,Yates04} have investigated different criteria for low power data transmission.
+Power consumption for data transmission in IEEE 802.11 multi-hop networks and 3G mobile wireless networks were analysed in \cite{Le11} and \cite{toorisaka12} respectively.
+In order to increase transmission speed and reduce power dissipation, parallel data transmission methods are widely used.
+However, parallel transmission is limited to short distance communications, e.g.
+locally connected devices, internal buses.
+Ruling out the possible availability of parallel transmission links over long distance, we are left with its serial alternative only.
+If we attempt to transfer big files, e.g.
+DNA sequences, over a serial transmission link then it would take a significant amount of time and obviously a significant amount power would be dissipated in the process.
+However, data compression techniques are widely used to reduce size of data before transmitting over serial medium to reduce transmission time and cost.
+
+Huffman code \cite{Huff51} is an entropy
+encoding algorithm widely used for lossless data compression.
+For any given set of symbols and associated occurrence probabilities, Huffman algorithm generates a binary tree (Huffman tree) to encode a message with an optimal number bits.
+The codeword for a distinct symbol is generated by traversing the tree from the root to
+the leaf node representing the symbol.
+In this traversal process, a move towards a left and a right node is represented by $0$ and $1$ respectively.
+To transmit a binary string, power dissipation  is proportional to the number of switching, i.e., transition from $0$ to $1$ and vice versa, present in a transmitted string.
+Although a number of approaches like \cite{Gol12,Kab14} have extended the classical Huffman code by considering the cost of $0$ and $1$ as unequal, a little effort has been given to address the switching activities in the Huffman code to develop a power efficient Huffman code.
+To the knowledge of the authors, the only effort to generate Huffman code considering switching activity is seen in \cite{Chen06}.
 \section{Background}

### 2015-02-23 Switche Paper 1st approache/elsarticle-template-num.tex
intro finished

@@
 \section{Introduction}
-In the recent years, application of battery-powered portable devices, e.g.
-laptop computers, personal digital assistant (PDA),  and mobile phones has increased significantly.
-The reliability and performance of such devices are primarily dependent  on their power consumption, e.g., effective battery life.
+In the recent years, application of battery-powered portable devices, e.g., laptop computers, personal digital assistant (PDA),  and mobile phones has increased significantly.
+The reliability and performance of such devices are primarily dependent  on their power consumption, i.e., effective battery life.
 Bigger battery size could help to improve power efficiency, however, in a portable device the size of the battery is restricted by the size and weight of the device itself.
-The cost of providing power both in portable and non-portable devices has resulted in significant interest in power reduction.
+The cost of providing power to both portable and non-portable devices has resulted in significant interest in power reduction.
 CMOS technologies were developed in order to reduce the power consumption both in data processing and transmission.
@@
 In this traversal process, a move towards a left and a right node is represented by $0$ and $1$ respectively.
+A major drawback of the classical Huffman code is that the whole stream must be read prior to encoding.
 To transmit a binary string, power dissipation  is proportional to the number of switching, i.e., transition from $0$ to $1$ and vice versa, present in a transmitted string.
-Although a number of approaches like \cite{Gol12,Kab14} have extended the classical Huffman code by considering the cost of $0$ and $1$ as unequal, a little effort has been given to address the switching activities in the Huffman code to develop a power efficient Huffman code.
+Although a number of approaches like \cite{Gol12,Kab14} have extended the classical Huffman code by treating binary bits differently (with unequal letter cost), a little effort has been made to optimise the switching activities in the Huffman code to develop a power efficient Huffman code.
 To the knowledge of the authors, the only effort to generate Huffman code considering switching activity is seen in \cite{Chen06}.
+This approach follows a greedy strategy and works in two steps to reduce total number of switching in the Huffman code.
+In the first step the switching activity between each pair of symbol (inter-switch) is reduced and then in the second step switching activity in the codeword for each each symbol (intra-switch) is reduced.
+As the optimisation is done independently in two steps therefore it is highly likely that the gain obtained in the first step may be compromised in the second step and vice versa.
+
+In this paper, a genetic algorithm based approach is proposed to reduce the total number of switching where inter-switch and intra-switch is optimised in a single step, i.e, a balance is made between the two different types of switching.
+The approach generates a set of trees, each one represents a set of codewords (solution).
+After that a set of genetic operators such as selection, crossover and mutation is used to evolute (create new trees) the population to minimise number of total switches.
+The evolution process is controlled by the total number of inter- and intra-switches.
+Inter-Switch between two adjacent symbols depend on the their codewords, i.e., how the codeword of the preceding symbol finished (with $0$ or $1$) and how the codeword for the descendent symbol started.
+If the end bit of the preceding symbol and the staring bit of the successor symbol differs then their exists a switch and the total number of switch is the number of times the two symbols in consideration occurs one after another.
+To obtain the total number Inter-Switch between pair of symbols, we used a descendent matrix which is a two dimensional matrix represents the number of occurrence of each symbol after another.
+This matrix is formed when the message to be transmitted is scanned to obtain the frequency of distinct symbols.
+The number of intra-switch for a symbol is calculated by multiplying the frequency of that symbol by the number of logic level transition ($0$ to $1$ or $1$ to $0$) in the codeword of the symbol.
+The efficiency of the approach is evaluated by applying it to a set of biological datasets.
+The experiments yield that the proposed approach improves the total number of switches by $X\%$ in the best case, by $Y\%$ in the average case and by $Z\%$
+in the worst case.
+
+The rest of the paper is organised as follows:
+Section 2 presents the background study of the
+relationship of switching activity with power consumption, the relation of switching with Huffman code and the issues in biological data transmission.
+The proposed approach is described in Section 3.
+Experimental results and
+discussion are presented in Section 4 . Finally,
+concluding remarks are presented in Section 5.
+
 \section{Background}

### 2015-02-23 Switche Paper 1st approache/elsarticle-template-num.tex
docs

@@
 %% Text of abstract
-
+Recently the power consumption identified as one of the most pressing challenges of data transmission.
+Though a considerable reduction of size of data is obtained by Huffman code and several methods have been proposed to improve the data compression rate.
+These methods improves only the total number of bits without consideration of transmission cost.
+In this paper, we propose a new approach to reduce the power consumption, by applying genetic algorithm for minimising the total number of switches, either inter- or intra-switch.
+The approach starts it operation by generating a set of trees considered as initial population for the genetic algorithm, each one of these trees represent a set of codewords (solution), after that the genetic operators such as selection, crossover and mutation will be applied to the initial population in order to evolute the quality of the solutions.
+The amount of power consumption is proportional to the total number of switches on the whole sequence.
+The performance of the approach is evaluated by applying it to compress some standard biological datasets.
+The experiments yield that the proposed approach improves the power consumption rate considerably comparing with classic Huffman code.
 \end{abstract}
@@
 concluding remarks are presented in Section 5. 
-
 \section{Background}
@@
 Genome 12& 17.59&11.86&32.57 \\\hline
-Genome 13& &&\\\hline
-Genome 14& && \\\hline
+Genome 13& 17.39&10.93&\\\hline
+Genome 14&18.53 &11.64& \\\hline
 Genome 15& && \\\hline

### 2015-02-23 Huffman Code with unequal letter cost and optimisation/Article.tex
good

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt]{elsarticle}%preprint,

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{algcompatible}
\usepackage{multirow}

%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}
\journal{Digital Signal Processing }
\bibliographystyle{elsarticle-num}
\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Optimised Cost Considering Huffman Code for
Biological Data Compression}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

%\author{}
\author[a,b]{Youcef Gheraibia\corref{cor1}}
\ead{Y.Gheraibia@hull.ac.uk}
\author[a]{Sohag Kabir\corref{cor2}}
\ead{s.kabir@hull.ac.uk}
\author[c]{Mohammad Kaykobad}
\author[d]{Abdelouahab Moussaoui}
\author[b]{Smaine Mazouzi}

\address[a]{Department of Computer Science, University of Hull, Hull HU6 7RX, UK}

\address[b]{Department of Computer Science, Badji Mokhtar-Annaba University, P.O. Box 12, 23000 Annaba, Algeria}

\address[c]{Department of Computer Science and Engineering, Bangladesh University of Engineering and Technology, Dhaka 1000, Bangladesh}

\address[d]{LRIA laboratory, Department of Computer Science, University of Setif, 19000, Algeria}

\cortext[cor1]{Corresponding author. Tel.: +44-7479-560709 ;}

\cortext[cor2]{Corresponding author. Tel.: +44-7405-024667 ; }

\begin{abstract}
%% Text of abstract
Classical Huffman code has widely been used to compress biological datasets. Though a considerable reduction of size of data is obtained by classical Huffman code, yet, more efficient encoding is possible by treating binary bits differently considering requirement of transmission time, energy consumption, and likewise. A number of techniques already modified Huffman code algorithm to  obtain optimal prefix-codes for unequal letter costs in order to reduce overall transmission cost (time). 
%In the recent year with the wide use of cloud and the distributed application in our life, the data transmission become more challenging over the years. 
In this paper we propose a new approach to improve compression performance of one such extension, cost considering approach (CCA),   %the data transmission technique by improving the representation of Huffman code with the use of a 
by applying genetic algorithm for optimal allocation of the codewords to the symbols. 
%The work in this research is consists of two steps. 
%The approach start with generating a set of codewords for different input symbols based on their frequencies by considering cost (length) of 0 and 1 as $\alpha$ and $\beta$,~$\alpha < \beta$. This step ensures optimal cost encoding, however, compression performance is not higher than classical Huffman code. 
%The aim of the codes generation method is to minimise the number of ones on the generated codes, which minimise the cost of the transmission. 
%To improve compression performance, the second part of the approach uses genetic algorithm to find an optimal allocation of generated codes to different symbols. 
The idea is to sacrifice some cost to minimise the total number of bits, hence, the genetic algorithm works by giving penalty on the cost. The performance of the approach is evaluated by applying it to compress some standard biological datasets. The experiments yield that the proposed approach improves the compression performance of the CCA considerably without increasing the cost significantly.%     and comparing the result with the results produced by classical Huffman code and cost considering Huffman code.
% The case study of the approach is the biological data, which present a good application area to data compression with the huge growth of the biological data bases. 
%The results are very promising and we have compared with the standard cost considering Huffman code and the original Huffman code.
\end{abstract}

\begin{keyword}
Data Compression, Huffman Code, Genetic Algorithm, Cost Considering Approach, Signal Processing.
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
\label{sec1}
In the recent years, application of battery-powered portable devices, e.g. laptop computers and mobile phones has increased significantly. Proper representation of digital data and their transmission efficiency has become a primary concern for digital community because it affects the performance, reliability, and the cost of computation in both portable and non-portable devices. CMOS technologies were developed in order to reduce the power consumption both in data processing and transmission. In order to increase transmission speed and reduce transmission cost, parallel data transmission methods are widely used. However, parallel transmission is limited to short distance communications, e.g. locally connected devices, internal buses. Ruling out the possible availability of parallel transmission links over long distance, we are left with its serial alternative only. If we attempt to transfer big files, e.g. DNA sequences, over a serial transmission link then it would take a significant amount of time. However, we cannot overlook this problem because at present parallel processing is widely used to increase throughput and in parallel processing architecture, processing units are usually distributed in different physical locations and task sharing is a must in such architecture.    
.
Data encoding techniques came into action to improve the data transmission efficiency over serial communication medium by compressing data before transmitting. Efficiency can be measured in terms of incurred cost, required storage space, consumed power, time spent and likewise. Data must be encoded to meet the purposes like: unambiguous retrieval of information, efficient storage, efficient transmission and etc. Let a message consist of sequences of characters taken from an alphabet $\Sigma$, where  $\delta_1,\delta_2,\delta_3\ldots,\delta_r$ are the elements that represent the characters in the source $\Sigma$. The length of $\delta_i$ represents its cost or transmission time, i.e., $cost\left(\delta_i\right)= length(\delta_i)$. A codeword $w_i$ is a string of characters in $\Sigma$, i.e., $w_i\in\Sigma^{+}$. If a codeword is $w_i=\delta_{i1},\delta_{i2},\ldots,\delta_{in}$, then the length or cost of the codeword is the sum of the lengths of its constituent elements:

\begin{equation}
\label{eqn1}
  \text{cost}\left(w_i\right)=\sum_{j=1}^{n}cost\left(\delta_{ij}\right)
\end{equation}

If all the elements of a codeword has unit cost or length then the cost of the codeword is equivalent to the length of the codeword. However, it is not necessary for the elements in the codeword to have equal length or cost. For example, in Morse Code all the ASCII characters are encoded as sequence of dots ($\cdot$) and dashes ($-$) where a dash is three times longer than a dot in duration \cite{Redmond09}. However, the Morse code scheme suffers from the prefix problem \cite{Gr03}. Ignoring the prefix problem, Morse code results in a tremendous savings of bits over ASCII representation. Using Morse code, we can treat the binary bits differently; 0 as a dot and 1 as a dash. Even if we consider the voltage level to represent the binary digits then they are still different. Table \ref{table1} shows the logic level to represent binary digits in CMOS and TTL technologies.

\begin{table}[h]
\renewcommand{\arraystretch}{1.5}
\caption{Example of binary logic level}
\label{table1}
\centering
\begin{tabular}{c c c c}
\hline
 \bfseries Technology  & 0 & 1&Notes\\
\hline
\bfseries CMOS & $0~V$ to $\frac{V_{DD}}{2}$&$\frac{V_{DD}}{2}$ to $V_{DD}$&$V_{DD}$= supply voltage\\
%\hline
\bfseries TTL & $0~V$ to $0.8~V$&$2~V$ to $V_{CC}$ &$V_{CC}$ is $4.75~V$ to $5.25~V$\\
%\hline
\hline
\end{tabular}
\end{table}

As the unequal letter cost problem is not new therefore it has been addressed by different researchers. The more general case where the costs of the letters as well as the probabilities of the words are arbitrarily specified was treated in \cite{Karp61}. A number of other researchers have focused on uniform sources and developed algorithm for the unequal letter costs encoding \cite{Gil95, Kar62,Varn71,AltMel80,perl1975}.  Let $p_1,p_2,\ldots,p_n$ be the probabilities with which the source symbols occur in a message and the codewords representing the source symbols are $w_1,w_2,\ldots,w_n$ then the cost of the code $W$ is:

\begin{equation}
C\left(W\right)=\sum_{i=1}^{n}cost\left(w_i\right).p_i 
\end{equation}
The aim of producing an optimal code with unequal letter cost is to find a codeword $W$ that consists of $n$ prefix code letters each with minimum cost $c_i$ that produces the overall minimum cost $C\left(W\right)$, given that costs $0<c_1\leq c_2 \leq c_2 \ldots \leq c_n$, and probabilities $p_1\geq p_2\geq \ldots\geq p_n>0$.

Huffman code\citep{Huff51} is an efficient data compression scheme that takes into account the probabilities at which different quantization levels are likely to occur and results in fewer data bits on the average. It is widely used to compress biological data, however, all the techniques use the classical form of the Huffman code where bits are treated equally. Out of many variations of the Huffman code where cost of bits are treated unequally, the most recent approach is described in \cite{Kab14}. This approach treated binary bit 0 as a dot $\left(\cdot\right)$ and 1 as a dash $\left(-\right)$ like Morse code and reduces the transmission cost (time) significantly. Like other variations of the cost considering Huffman code, the compression performance (in terms of number of bits require to encode a message) of this approach is not also better than classical Huffman code. In this paper, we have proposed a new optimised cost considering Huffman code based on the approach shown in \cite{Kab14}. This new approach optimised the number of bits require to encode biological datasets while treating the binary bits unequally. The codewords generated by the approach described in\cite{Kab14} only considers cost reduction but ignores bits reduction therefore number of total bits are considerably high. The proposed approach aims at reducing total number of bits   by applying a genetic algorithm. The algorithm works by giving penalty on cost to reduce number of bits, but also ensures that the overall cost is lower than classical Huffman code.  The efficiency of the method is evaluated by applying it to compress some standard biological datasets.

The rest of the paper is organised as follows: Section~\ref{sec2} presents the background study of the issues in biological data processing and the Huffman code. The proposed approach is described in Section~\ref{sec3}. Experimental results and discussion are presented in Section~\ref{sec4} . Finally, concluding remarks are presented in Section~\ref{sec5}.

\section{Background}
\label{sec2}
\subsection{Issues in Biological Data Transmission}
The size of biological data including DNA sequences increase with an ever expanding rate and will be bigger and bigger in the future. These biological data are stored in biology databases. The exponential growth of these databases become a big problem to all biological data processing methods~\cite{Doug08}.
Different operations are applied to these data such as searching ~\cite{val10},e-mail attachment~\cite{chr09}, alignment ~\cite{che03}, and transmission on distributed computing platform~\cite{cha14}. Interestingly, biological data compression can play a key role in all sort of biological data processing.

A recent deluge of interest in the development of new tools for biological data processing requires efficient methods for data compression. The main objective of data compression methods is minimising the number of bits in the data representation. 
In ~\cite{bra09}, authors proposed a new general data structure and data encoding approach for the efficient storage of genomic data. This method encodes only the differences between a genome sequence and a reference sequence. For encoding, the method uses different fixed-length encoding schemes such as Golomb\cite{Golomb96}, Elias codes\cite{Elias75} and variable codes such as Huffman codes. There are other methods based on the same idea of encoding only the difference between reference sequence and the target one. One such approach~\cite{chr09} uses Huffman code for encoding difference between sequences to sent it as an email attachment. The main limitation of this method is that it must send the reference sequence for at least once for each species, and usually this sequence is too big to be sent as an email attachment.
Wang and Zhang \cite{wan11} proposed a new scheme for referential compression of genomes based on the chromosome level. The algorithm searches for longest common subsequence between two sequences and then the differences between them are encoded using Huffman code.
All previous studies focus only on the differences and the relation between continuation of the sequence, and use existing encoding approaches to encode biological datasets without considering possible improvement of the encoding schemes.

%\subsection{Rationale of Unequal Bit Cost Considering Encoding Approaches}

\subsection{Huffman Codes}
In computer science and information theory, Huffman code is an entropy encoding algorithm used for lossless data compression. It takes into account the probabilities at which different symbols are likely to occur and results into fewer data bits on the average. 
%then assigns variable-length codes to different distinct symbols, and thus minimises the number of bits required to encode a message. 
For any given set of symbols and associated occurrence probabilities, there is an optimal encoding rule that minimises the number of bits needed to represent the source. Encoding symbols in predefined fixed length code, does not attain an optimum performance, because every character consumes equal number of bits irrespective to their degree of contribution to the whole data. Huffman code tackles this by generating variable length codes, given a probability usage frequency for a set of symbols. It generates prefix-code to facilitate unambiguous retrieval of information. A scheme of prefix code assigns codes to letters in $\Sigma$ to form codeword $w_i$ such that none of them is a prefix to another. For example, the codes $\left\{ 1,01,001,0001\right\}$ and $\left\{ 000,001,011,111\right\}$ are prefix-free, whereas the code $\left\{ 1,01,100\right\}$ is not, because 1 is a prefix in 100.

Applications of Huffman code are pervasive throughout
computer science. The algorithm to completely perform Huffman encoding and decoding is explained in \cite{Amst86}. It can be used effectively where there is a need for a compact code to represent a long series of a relatively small number of distinct bytes. For example, Table \ref{table2} shows 8 different ASCII characters, their frequencies, ASCII codes and the codewords generated for those symbols using Huffman code. It is seen from the table that the codeword to represent each character is compressed and the most frequent character gets the shortest code. In this example, the compression ratio obtained by Huffman code is 64.16\%.

\begin{table}[h]
\renewcommand{\arraystretch}{1.3}
\caption{Example of application of Huffman Code to compress ASCII characters}
\label{table2}
\centering
\begin{tabular}{c c c c}
\hline
 Symbols & Frequency& ASCII Code &\begin{tabular}{@{}c@{}}Codewords using\\Huffman Code\end{tabular} \\
\hline
\bfseries A & 50&01000001&00\\
%\hline
\bfseries B & 35&01000010&101\\
%\hline
\bfseries C & 42&01000011&110\\
%\hline
\bfseries D & 22&01000100&1001\\
%\hline
\bfseries E & 65&01000101&01\\
%\hline
\bfseries F & 25&01000110&1111\\
%\hline
\bfseries G & 9&01000111&1000\\
%\hline
\bfseries H & 23&01001000&1110\\
\hline
\end{tabular}
\end{table}

There are many other variants of Huffman codes that compress source data to reduce data size and/or transmission cost. For example, Mannan and Kaykobad\cite{Kay03} introduced block technique in Huffman coding which overcomes the limitation of reading whole message prior to encoding. In the classical Huffman coding scheme, the letter costs are considered as equal. The unequal letter cost versions of Huffman codes scheme are proposed in \cite{Gol1996,Gol02,Gol2002,Gol12}.
In these versions, letters  of  the alphabet  are  treated  unequally. Recently, in \cite{Kab14} a method is proposed to show the effects of unequal bits cost on classical Huffman code. The idea of this method is to assign the most frequent symbol the minimum cost code and the least frequent symbol the maximum cost code, whereas classical Huffman code assigns most frequent symbol the minimum length code and the least frequent symbol the maximum length code. As a result, the approach in \cite{Kab14} produces an optimal prefix-codes for unequal letter cost, thus reduces the overall (transmission) cost of the encoded data.

\section{The Proposed Approach}
\label{sec3}
%\subsection{}

A genome is a stretch of DNA that encodes  a polypeptide (protein)which is a set of amino acids bound together in a specific order. Each genomic sequence consists of nucleotides bound together, which are interpreted by the cellular machinery in groups of three, called triplets~\cite{Harvey00}. This is the main reason to divide the whole sequence in a set of triplet and give a code to each triplet. As each DNA sequence contains a combination of four nucleobases\textemdash guanine (G), adenine (A), thymine (T), and cytosine (C), therefore we will have $4^3=64$ possible triplets.  The first step in the optimised cost considering algorithm is cutting the genome sequence in triplets, then compute the frequency of each triplet in the whole sequence. This table of frequencies are used by the cost considering Huffman code to generate minimal cost code for each triplet (frequency). Finally, these codes with frequencies are used by the optimised cost considering algorithm to generate the optimal allocation with a given  penalty on cost. The whole process is shown in Fig.1.%\ref{Fig1}.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{Images/Drawing3_1.jpg}
\caption{The proposed scheme}
\end{center}
\label{Fig1}
\end{figure}

\subsection{Cost Considering Approach of Huffman code}
The classical Huffman algorithm aims at reducing total number of bits and it constructs a tree in a bottom up fashion. It is shown in \cite{golin98} that if the costs of letters are considered unequal then the straightforward bottom up greedy approach does not work. Authors in \cite{Kab14} uses a top down approach to build a binary tree considering unequal letter cost of bits. They considered cost (length) of 0 and 1 as integer constants $\alpha$ and $\beta$,   $\alpha < \beta$. Using the analogy of Morse code's `$\cdot$' and `$-$', the value of $\alpha$ and $\beta$ is set as 1 and 3 respectively. The complete algorithm to obtain an optimal prefix-free code for unequal letter cost is shown below (algorithm 1). The input to the algorithm are the distinct triplets contained in the genome sequence to be encoded and their frequencies. The process of creating the binary tree starts with a single node (root node) and it is initialised with cost 0.  After that, two child (leaf) nodes are created for the root node, i.e., level of the tree is increased by one. Cost of the left child is calculated as the summation of the cost of its parent node and the length of the left arc, and cost of the right child is calculated as the summation of the cost of its parent node and the length of the right arc. Length of left and right arcs are actually the cost (length) of 0 ($\alpha$) and 1 ($\beta$) respectively. The next step is to take a child node with least cost and create two child nodes for it and make it a parent node. In this way, in every iteration the child node with least cost becomes a parent node with two new child nodes. Creation of new child nodes is stopped when total number of child nodes become equal to the number of distinct triplets needed to be encoded.

\begin{algorithm}[!btph]
\caption{Cost Considering Algorithm (CCA)}
\label{alg1}

\begin{algorithmic}[1]
\REQUIRE Distinct symbols contained in the message to be encoded and their frequencies 
\ENSURE Non-uniform\ /\ variable\ letter\ cost\ i.e,\ Cost-considering\ balanced\ tree

\FOR{each distinct symbol $i$} 
\STATE $ Enqueue\left(max\_Q , frequency~[~i~]\right)$
\ENDFOR
\STATE create a root node
\STATE $cost~[~root~]\leftarrow 0$
\STATE $Enqueue\left(min\_Q , cost~[~root~]\right)$
\STATE Define costs of the left and right child of the binary tree
\REPEAT 
\STATE $cost\_of\_parent\_node\leftarrow Dequeue\left(min\_Q\right)$
\STATE create $left$ and $right$ child for this node
\STATE $cost~[~left\_child~]\leftarrow cost\_of\_parent\_node+left\_child\_cost$
\STATE $Enqueue\left(min\_Q , cost~[~left\_child~]\right)$
\STATE $cost~[~right\_child~]\leftarrow cost\_of\_parent\_node+right\_child\_cost$
\STATE $Enqueue\left(min\_Q , cost~[~right\_child~]\right)$
\STATE Mark parent node as explored
\UNTIL{$2\left(n-1\right)$ nodes are created}
\WHILE{$min\_Q\neq\emptyset$} 
\STATE $leaf\_node\leftarrow Dequeue\left(min\_Q\right)$
\STATE $frequency[leaf\_node]\leftarrow Dequeue\left(max\_Q\right)$
\ENDWHILE
\FOR{each parent node $j$} 
\STATE $frequency~[~j~]\leftarrow frequency~[~left\_child~]+frequency~[~right\_child~]$
\ENDFOR
\REPEAT
\IF{conflict between nodes} 
\STATE resolve conflict by swapping conflicted nodes
\STATE calculate and reassign cost of all affected nodes
\STATE calculate and reassign frequency of all affected nodes 
\ENDIF
\UNTIL{all conflicts are resolved }
%\algstore{myalg}
\end{algorithmic}
\end{algorithm}

Now the tree $T$ is constructed and the cost of the tree actually depends on how the frequencies are assigned to the leaf nodes. The overall cost will be minimised if the leaves with highest cost always have smaller or equal weight (frequency). To fulfil this condition the leaves of the $T$ are enumerated in non-decreasing order of their cost, i.e., $cost(l_1)\leq cost(l_2)\leq \ldots \leq cost(l_n),$ and that $f_1 \geq f_2 \geq \ldots\geq f_n$, where $l_i$ and $f_i$ are leaf nodes and frequencies of distinct triplets respectively $for~ i=1,2,\ldots n$ . The frequency or weight of parent nodes are calculated as the sum of the frequencies of its child nodes, and it continues upwards until the root node is reached. After that, the algorithm checks for any possible conflicts between all pair of nodes. Two nodes are considered as conflicted if the node with a higher cost has higher frequency violating the above condition, i.e., if $cost(l_i)> cost(l_j)~and~f(l_i)>f(l_j)$, then there remains a conflict.  If there remains a conflict between nodes, then it is resolved by swapping the nodes and recalculating the cost of the tree downward and frequency of the nodes upward.  When all the conflicts if existed are resolved then the algorithm generates codes for each of the distinct triplets.

\subsection{Optimisation of the Codes}
\subsubsection{Problem formulation}
The problem of finding the best allocation of codes to each triplet can be   modelled as an assignment problems, the problem is formulated as follows :\\\\
\textbf{Definition:} Given a set of codes $C=\left\{C_{1},C_{2}...C_{n}\right\}$, and a set of frequencies $F=\left\{F_{1},F_{2}...F_{n}\right\}$. For each code we have the length of the code $|C_{i}|$ (number of bits) and the cost of the code $S_{C_{i}}$, the objective is to assign to each frequency a code in order to minimise the total number of bits, while respecting the initially assigned total cost $S_{t}$ with a given penalty $\lambda\rightarrow [0,1]$. This penalty coefficient represents the allowed amount of cost that can be sacrificed to optimise the total number of bits.    
\\
The Objective Function is to:

\begin{equation}
Minimise \sum (|C_{i}| \times F_{j})
\end{equation}
while :
\begin{equation}
\sum (|S_{C_{i}}| \times F_{j}) \leqslant (\lambda+1) S_{t} 
\end{equation}

\subsubsection{Basic Genetic Algorithm}
Genetic Algorithm (GA) is a bio-inspired meta-heuristic algorithm developed by \cite{gen1}. GA is a stochastic optimisation algorithm imitate the natural evolution process of genomes. GA started by generating an initial population of random feasible solutions. The optimisation process of GA takes the initial population and generates a new population based on it.  The process can be described as follow:\\ 
Firstly, select two or more solutions from the current population by using one of the well-known selection techniques \cite{bli95}. These selected solutions will be considered as  parents. The second operation of the genetic algorithm is the crossover, which takes these parents as inputs to generate other new solutions considered as children. The third operation of the genetic algorithm is the mutation which ensures a good diversification in the search process. The new solutions can be mutated according to a given mutation probability. The mutation operation changes the value of one or more positions in the solution. The quality of each solution is verified by the fitness function which controls the evolution of the GA population by deletion of the worst solutions and insertion of the good solutions among  parents and sons. This processes is repeated until the stopped criteria is reached which can be the number of generation or if the population is stabilised.

\subsubsection{Optimised cost considering algorithm}
The main objective of the optimised cost considering algorithm (OCCA)is to apply GA to find an optimal allocation of the codewords to each triplets to reduce the total number of bits. In GA, the encoding of the solution into a chromosome is one of the most important issues in obtaining good optimisation results. The OCCA uses two fixed length arrays of size ``64" which is the number of combination for all nucleotides. The first array contains the frequencies of each triplets and the second array contains the cost of the codewords assigned to each triplets. Our genetic algorithm utilises the two arrays and uses the index of each entries in the allocation process.

The genetic algorithm is a stochastic algorithm based on random evolution process. The algorithm 2 describes the outline of the OCCA.   Generally the initial population is generated in a random affectation of codes to different triplets. In the OCCA algorithm, the population contain firstly the affectation given by the CCA. The rest of the population are randomly generated, all these generated solutions must satisfy the initial cost constraints, which is the cost ($S_t$) of the solution produced by CCA  and previously added to the population with a give penalty (step 1).

The evolution of the population is the key of the genetic optimisation algorithm. During each generation the process start with the selection of a part (set of solutions) of the population to bread a new generation. In the literature many selection methods have been proposed to guide the population evolution \cite{bli95}. The different methods for selecting a part (set of solutions) of the population vary from a random selection method to heuristic based selection method. We have chosen to select randomly the part of the population to be processed as the heuristic methods are very time-consuming (step 3).
After that the operations of genetic algorithm is applied on the initial population to generate a new generation of the population (see Fig.2). Firstly the crossover operation is applied to these two selected solutions (considered as parents) to generate two new solutions (considered as children)(step 4). In the literature many crossover techniques have been used in genetic algorithm \cite{osa14}, such as one-point crossover which divides the chromosomes into two fragments and recombines the second fragments with the other chromosome's second fragment. The two-point crossover divides the chromosomes into three fragments and recombines the middle fragment with  the middle fragment of the other chromosome. There are many other crossover techniques to allow a good convergence of the algorithm. In our case, we have used the two point crossover with two parameters, the first parameter $p_{c}$ is a random value in [0,63], which represents the first cut point and the second parameter $p_{m}$ is also a random value in [0,63], which represents the number of positions to be crossed. These two random parameters are to ensure a good diversification on the whole search space (step 4).

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.5]{Images/Drawing2.jpg}
\caption{Operations of genetic algorithm}
\end{center}
\label{Fig3}
\end{figure}

\begin{figure}[!thpb]
\begin{center}
\includegraphics[scale=0.55]{Images/Drawing_1.jpg}
\caption{Population update for genetic algorithm}
\end{center}
\label{Fig2}
\end{figure}

\begin{algorithm}[!thpb]
\caption{Optimised Cost Considering Algorithm (OCCA)}
\begin{algorithmic}[1]
\State Population initialization (P).
\REPEAT  
\State Select two solutions $S_{1},S_{2}$ form P.
\State Crossover $S_{1},S_{2}$ to generate $S_{11},S_{21}$ (Children).
\State Mutate $S_{11},S_{21}$.
\State Validate children with cost constraint (equation 4). 
\State Add children to population
\State Rank the population by fitness
\State Remove worst candidates until population limit
\UNTIL{Max number of generation not achieved} 
\EndWhile
\State Display the best solution from the population P;
\end{algorithmic}
\end{algorithm}

After the crossover operation, the newly generated children may contain conflict, for example, a single code is allocated to two different frequencies in the solution. To overcome such a conflict, a regulation operation is performed to refine the solution to ensure the correctness of the solution (see Fig.2).
 Secondly these two new solutions are mutated according to a predefined probability $\gamma$, the best value of the mutation rate is very problem specific (step 5). In our case, the value of $\gamma$ is fixed to $0.2$ to explorer a few positions in the solution. The mutation operator is used to maintain genetic diversity from one generation of the population of genetic algorithm to the next. In our case, we have used the mutation as a random swap mutation operator (see Fig.3).  Each newly generated solution must satisfy the cost constraint. The next step is to add these two new solutions (children) to the current population (step 7) (see Fig. 3). Finally, the new population are ranked by fitness (step 8), and the worst solutions are deleted until the initial size of the population is obtained  (step 9). The whole processes are repeated until the maximum number of operation is performed (step 10).

\section{Results And Discussion}
\label{sec4}
The effectiveness of the approach has been evaluated with different real genomic biological data, these genomes were downloaded from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$ \cite{pruitt2009ncbi}. We focused on the sequences alone, ignoring any header and any other exogenous information. In table 3, the different data sets are described with the size  of each of them in megabytes (MB) and the references on the biological data bank.

\begin{table}[!thpb]

\small
\label{table3}
\caption{Datasets description}
%\begin{center}
\centering
\begin{tabular}{c  c  c c}
\toprule
$\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size (MB)}$ &	$\textbf{Reference}$ \\\hline
Genome 1& Mycobacterium smegmatis &  6.66 & CP009496  \\\hline

Genome 2& Amycolatopsis benzoatilytica & 8.30 & NZ\_KB912942 \\\hline

\multirow{2}{*}{Genome 3}&Mycobacterium rhodesiae& \multirow{2}{*}{6.11} & \multirow{2} {*}{CP003169}\\ 
&NBB3& &\\
\hline

\multirow{2}{*}{Genome 4 }&Streptomyces bottropensis& \multirow{2}{*}{8.54} &
\multirow{2}{*}{NZ\_KB911581} \\ 
& ATCC 25435 \\
\hline

\multirow{2}{*}{Genome 5}&Mycobacterium smegmatis& \multirow{2}{*}{ 6.66} &\multirow{2}{*}{CP009494             } \\ 
&str. MC2 155 \\
\hline

\multirow{2}{*}{Genome 6}&Mycobacterium smegmatis& \multirow{2}{*}{6.76} &\multirow{2}{*}{NZ\_KI421511}\\   &MKD8& &\\
\hline

Genome 7& Bradyrhizobium WSM471&  7.42 &NZ\_CM001442\\\hline

\multirow{2}{*}{Genome 8}&Amycolatopsis thermoflava&  \multirow{2}{*}{8.27} &\multirow{2}{*}{NZ\_CM001442}\\   &N1165 & \\
\hline

\multirow{2}{*}{Genome 9}&Bacillus thuringiensis&   \multirow{2}{*}{5.74} &\multirow{2}{*}{ NZ\_CM000747 }\\    &Bt407&\\
\hline

\multirow{2}{*}{Genome 10}&Bacillus thuringiensis& \multirow{2}{*}{6.03} &\multirow{2}{*}{ NZ\_CM000748}\\    &serovar thuringiensis& \\
\hline

\multirow{2}{*}{Genome 11}&Pseudomonas aeruginosa& \multirow{2}{*}{6.48} &\multirow{2}{*}{NZ\_AFXI01000001}\\    &9BR&\\
\hline

\multirow{2}{*}{Genome 12}&Bacillus thuringiensis&  \multirow{2}{*}{5.97} &\multirow{2}{*}{ NZ\_CM000753}\\    &serovar berliner ATCC &\\
\hline

\multirow{2}{*}{Genome 13}&Bacillus thuringiensis& \multirow{2}{*}{5.75} &\multirow{2}{*}{ NZ\_CM000750 }\\    &serovar pakistani&\\
\hline

\multirow{2}{*}{Genome 14}&Pseudomonas aeruginosa& \multirow{2}{*}{6.28} &\multirow{2}{*}{CP006982}\\    &LES400&\\
\hline

\multirow{2}{*}{Genome 15}& Mus musculus & \multirow{2}{*}{25.58} &\multirow{2}{*}{GL456087}\\  &chromosome 1&\\
\hline

\multirow{2}{*}{Genome 16}& Danio rerio & \multirow{2}{*}{56.14} &\multirow{2}{*}{CM002885}\\ & chromosome 1 &\\
\hline
\multirow{2}{*}{Genome 17}&Homo sapiens & \multirow{2}{*}{76.64 } &\multirow{2}{*}{  CM000680  }\\    & chromosome 18 &\\
\hline
\multirow{2}{*}{Genome 18}&Homo sapiens & \multirow{2}{*}{99.94} &\multirow{2}{*}{CM000684   }\\ & chromosome 22&\\
\hline
%\bottomrule
\end{tabular}
%\end{center}
\end{table}

\begin{table}[h]
\renewcommand{\arraystretch}{1.1}
\small
\label{table4}
\caption{Comparison of performance among classical Huffman code, CCA, and OCCA without penalty}
%\begin{center}

\begin{tabular}{c  c c  c c  c c}
\hline
 & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{CCA }& \multicolumn{2}{c}{OCCA \textit{($\lambda$=0)}}\\\hline
$\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Size(MB)}$ &	$\textbf{Cost}$&	$\textbf{Size(MB)}$&$\textbf{Cost}$&	$\textbf{Size(MB)}$
\\\hline
Genome 1& 76787151  &	4.44	&67416213   & 4.92	& 67416213 & 4.82 \\\hline
Genome 2& 100425402 &  	5.81	& 88430665	& 6.51	& 88430665&  6.35 \\\hline
Genome 3& 75940155  &	4.39    &66745619	& 4.87&	66745619 & 4.79 \\\hline
Genome 4& 103552729 &	5.96    &90821835&	6.69 &	90821835  & 6.47\\\hline
Genome 5& 82234926  &	4.74	&71963876	& 5.27 &	71963876 &5.17 \\\hline
Genome 6& 83454842  &   4.81	&73038795	& 5.34	&73038795 & 5.24\\\hline
Genome 7& 92539488  &	5.36    &81416359   &5.93	&81416359 & 5.85\\\hline
Genome 8& 99613856  & 	5.74	&87102639   &6.41	&87102639&	6.30 \\\hline
Genome 9& 71876739  &	4.15    &62998800  &4.58 &	62998800 &	4.49 \\\hline
Genome 10& 75324432 & 	4.36	&66084958  &4.81	&66084958&	4.73 \\\hline
Genome 11& 80766360 &	4.66    &70620666  &5.41&	70620666&	5.04 \\\hline
Genome 12& 74560825 &	4.31    &65359604  &4.75	&65359604&	4.67\\\hline
Genome 13& 71562941 & 	4.14	&62758225  &4.56	&	62758225 &	4.50\\\hline
Genome 14& 78261299 & 	4.51    &68354090  &4.8&	68354090& 4.89  \\\hline
Genome 15& 324439242& 	18.77    &286008420 & 20.66	 &	286008420 &	19.94 \\\hline
Genome 16& 703734840&  40.77    &618859291 & 45.08  &	618859291 &	43.18 \\\hline
Genome 17& 901032667&  52.08    &791840455 &	57.36 &	791840455 &	55.12 \\\hline
Genome 18& 983434816&  56.98    &867299889 &	62.42 &	867299889 & 60.70 \\\hline

%\bottomrule
\end{tabular}
%\end{center}
\end{table}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.45]{Images/drawing4_1.jpg}
\caption{Convergence of OCCA for \textit{Genome 2}}
\end{center}
\label{Fig5}
\end{figure}

\begin{table}[tpbh]
\small
\renewcommand{\arraystretch}{1.1}
\caption{Effects of  the penalty on the compression performance of the OCCA}
%\begin{center}
\centering
\begin{tabular}{c c c c c }
\toprule
$\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Size(MB)}$ &		\textbf{$\lambda (\%)$} &		\textbf{Compression ratio $\%$} \\\hline
Genome 1 &	 70760174 &4.50& 4\% & 32.72\%\\\hline
Genome 2 &	92010490& 5.91 & 5\%& 28.79\%\\\hline
Genome 3&	69421783& 4.47 &3\%& 26.84\%\\\hline
Genome 4&	96294638& 5.99 & 5\%& 29.85\%\\\hline
Genome 5&	74855668 &4.81& 5\%& 27.77\%\\\hline
Genome 6&	76738330& 4.86  &4\%& 28.10\%\\\hline
Genome 7&	84667949 &5.47& 3\%& 26.28\%\\\hline
Genome 8&	92416243 &5.76& 5\%& 30.35\%\\\hline
Genome 9&	66145783&4.21 & 4\%& 26.65\%\\\hline
Genome 10&	68751359& 4.44 &3\%& 26.63\%\\\hline
Genome 11&	72737300 &4.79& 2\%&26.08\%\\\hline
Genome 12&	67981988 & 4.38&3\%& 26.63\%\\\hline
Genome 13&	65896779& 4.18 &4\%& 27.30\%\\\hline
Genome 14&	71762305 &4.55 &4\%&27.54\% \\\hline
Genome 15&297188002 &19.31 & 3\%& 24.51\%\\\hline
Genome 16&643785655 & 41.68 & 3\%& 25.75\% \\\hline
Genome 17&823506882 & 53.05 & 3\%& 30.78\%\\\hline
Genome 18&901515198 &58.99 & 3\%& 40.97\%\\
\bottomrule
\end{tabular}
%\end{center}
\label{table5}
\end{table}

Table~\ref{table4} presents the results obtained by the classical Huffman code, the cost considering algorithm (CCA) and the optimised cost considering algorithm (OCCA) without penalty on cost. The results show that the number of bits required by the classical Huffman algorithm to encode genomic data is the minimum among the other algorithms but the cost is  maximum. The cost considering algorithm improves the representation of the generated codes in terms of cost but the number of bits. However, still it compresses the data by $37.54\%$ in the best case, $16.51\%$ in the worst case, and $22.08\%$ on an average. In terms of cost, in the best case the CCA improves cost over classical Huffman code by $12.66\%$, in the worst case by $11.80\%$, and on an average by $12.24\%$.  The optimised cost considering algorithm tries to find the best allocation of codes to frequencies by giving penalty on cost. The outcome of this process is a fall in the total number of bits and a rise in the total cost. However, the cost is always lower than the cost incurred by the classical Huffman algorithm.  At first, the OCCA optimises number of bits without applying any penalty on the cost (see table 4). Afterwards, it continues giving penalty ranging from 1\% to 10\% on the cost  until a balance is found between total cost and bits. Fig. 4 shows the convergence of the OCCA for minimising number of bits for genome 2 according to the cost constraint. For each genome, a maximum amount of effective penalty is identified, after this maximum value, increasing the penalty is not helping any more to reduce number of bits, i.e., number of bits reach to minimum and cost to maximum.  The table \ref{table5} presents the best founded number of bits for different datasets with different effective penalty. As seen in the table, the OCCA improves the compression ratio from $37.54\%$ to $40.97\%$ in the best case, from $16.51\%$ to $24.51\%$ in the worst case, and from $22.08\%$ to $28.53\%$ in the average case. This is evident from the table 5 that this improvement is obtained without increasing the cost significantly.    %are in-useful (See figure 3), the number of bits achieve the minimum number but the cost stop decreasing (point 1 in figure 3) and this number of bits stabilized while the cost still increasing until it stabilized also (point 2 figure 3), after this point the cost and number of bits are stabilized.

\section{Conclusion}
\label{sec5}
In this paper, we have discussed how the cost considering  algorithm (CCA) of Huffman code~\cite{Kab14} can be used to efficiently compress  biological datasets to facilitate efficient data transmission. The advantage of CCA is that it significantly improves (transmission) cost over classical Huffman code given that the cost of bits are different, however, it takes more bits than the classical Huffman code to encode data. In this paper, we identified genetic algorithm as a potential method to optimise the total number of bits in the CCA. The proposed optimised cost considering approach (OCCA) starts its operation by generating a set of optimal prefix-free codewords for a set of distinct input symbols by applying CCA which treats binary bits unequally.

 After that, the approach utilises genetic algorithm to find an optimal allocation of generated codewords to different symbols to reduce the total number of bits require to encode the dataset. In this allocation process the OCCA gives penalty on the cost to improve the compression performance.

The proposed approach is applied to biological genomic datasets and a performance comparison is made with the standard Huffman code and the cost considering algorithm of the Huffman code. The results show that the proposed approach improves the compression performance of the CCA significantly without affecting the cost notably. In future, we hope to extend this work by reducing number of switching activity between the codewords to further reduce the cost of transmission.
%is more robust and efficient compared to other competing algorithms because its penalty based optimisation strategy to search the best allocation of codes to different frequencies.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix
%% \section{}
%% \label{}
%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-num} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

%\begin{thebibliography}{00}

%% \bibitem{label}
%% Text of bibliographic item

%\bibitem{}

%\end{thebibliography}

\section*{References}
\bibliography{mybibfile}
\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2015-02-23 Switche Paper 1st approache/elsarticle-template-num.tex
exprimernts+ conlusion

@@
 \subsection{Issues in Biological data transmission}
-The size of biological data base increase with an expanding rate and it doesn't stop for increasing.
-In the last decade the use of biological data history increase which evolve a high request to data from this high volume biological data base.
+The size of biological data base increase with an expanding rate and it doesn't stop for increasing .
+In the last decade the use of biological data history increase which evolve a high request to data from this high volume biological data base [].
 The exponential growth of these databases become a big problem to all biological data processing methods.
@@
 Furthermore, the mutation provide the diversity on the search space solution by changing the position of  nodes on the same tree.
-After these two operations, the next step of the genetic algorithm is two to breed the new population.
+After these two operations, the next step of the genetic algorithm is two to breed the new population (see fig.2).
 Firstly the new solutions (children) are added to the current population, after that the population is ranked by fitness.
@@
 \label{Fig1}
+\end{figure}
+\begin{figure}[tbph]
+\begin{center}
+\includegraphics[width=350pt,height=170pt]{Images/Drawing3.jpg}
+\caption{Population update for genetic algorithm}
+\end{center}
+\label{Fig2}
 \end{figure}
@@
 Genome 12& 17.59&11.86&32.57 \\\hline
-Genome 13& 17.39&10.93&\\\hline
-Genome 14&18.53 &11.64& \\\hline
-Genome 15& && \\\hline
-Genome 16&&& \\\hline
-Genome 17& && \\\hline
-Genome 18& && \\\hline
-
+Genome 13& 17.39&10.93&37.14\\\hline
+Genome 14&18.53 &11.64&37.18 \\\hline
+Genome 15&78.19 &50.60&35.28 \\\hline
+Genome 16& & & \\\hline
+Genome 17& & & \\\hline
+Genome 18& & & \\\hline
 %\bottomrule
@@
 \section{Conclusion}
+In this paper we described how the genetic algorithm can be used to improve the power consumption in biological data transmission.
+The advantage of the proposed approach is that it minimise considerably the number of switches with affect directly the power consumption for data transmission.
+In this paper, we identified genetic
+algorithm as a potential method to optimise the total number of inter- and intra-switches.
+The Genetic algorithm start by generating a set of feasible solutions (trees), each one contain a set of codewords.
+After that, the approach uses the natural genetic operators to improve the quality if the solutions by generating new solution.
+the evolution of the population is controlled by the number of switches both inter- and intra-switches.
+The proposed approach is applied to biological data sets with different sizes from small genome to a human chromosome.
+The approach has been compared with the classic Huffman code.
+The results show that
+the proposed approach improves the power consumption rate considerably.
+The experiment shows that the proposed approach improves Huffman code in the best case with $best$,  $average$ in the average case, and $worst$ case.
+For the future we hope to improve the allocation of codewords to different frequencies in orderer to improve the total number of switches.
 

### 2015-02-24 Switche Paper 1st approache/elsarticle-template-num.tex
new version

@@
 \subsection{Issues in Biological data transmission}
-The size of biological data base increase with an expanding rate and it doesn't stop for increasing .
-In the last decade the use of biological data history increase which evolve a high request to data from this high volume biological data base [].
-The exponential growth of these databases become a big problem to all biological data processing methods.
+The size of biological data base increase with an expanding rate and it doesn't stop for increasing.
+In the last decade the use of biological data history increase which evolve a high request to data from this high volume biological data base~\cite{Doug08}.
+The exponential growth of these databases become a big problem to all biological data processing methods~\cite{Doug08}.
 Data compression methods is the most used methods to evolve the reduce the cost of treatment of high volume data bases.
 The main objective of data compression methods is minimising the number of bits in the data representation.
-Authors in [] proposed a new approach to genomic data compression based in suffix and common substring and code the difference with Huffman code.
-In [16], authors propose a general scheme for coding only the difference between the target genome and the referential one, the coding method used is Huffman.
-Recent work on data compression for biological data have been proposed to deal with transmission of genomic data as an email attachment [][][].
+Authors in~\cite{bra09} proposed a new approach to genomic data compression based in suffix and common substring and code the difference with Huffman code.
+In~\cite{chr09}, authors propose a general scheme for coding only the difference between the target genome and the referential one, the coding method used is Huffman.
+Recent work on data compression for biological data have been proposed to deal with transmission of genomic data as an email attachment~\cite{wan11}.
 Cost of data transmission is based on two point, firstly the size of the data which has been improved considerably in the recent year with the improvement of Huffman code.
@@
 \section{GA-SO : Genetic algorithm for Switches Optimising}
-Genetic algorithm (GA) is one the of the most popular bio-inspired meta-heuristic algorithm inspired from the natural evolution of species [].
+Genetic algorithm (GA) is one the of the most popular bio-inspired meta-heuristic algorithm inspired from the natural evolution of species~\cite{gen1}.
 It is a  population based algorithm starts with the generation of a random initial population.
@@
 \subsection{Preparing data and population generation}
-Huffman algorithm read the whole message to compute frequencies.
-The proposed algorithm read the whole genome to generate the frequencies of the triplet and by the way to generate the adjacent matrix which represents the frequencies precedence of between triplet.
+A genome is an expansion of DNA sequence which is a set of nucleotides that encodes a protein.These nucleotide are bounded together and each order define a specific protein.
+The transformation of DNA sequence to protein  is made by the cellular machinery, each three nucleotides are interpreted to a specific amino acid this three nucleotide are called triplets~\cite{Harvey00}.
+Huffman algorithm read the whole message to compute frequencies, the proposed algorithm read the whole genome and cut it into triplet to generate the frequencies of the triplet and by the way to generate the adjacent matrix which represents the frequencies precedence between triplet.
 The initial population is generated randomly, each solution on the population represents a tree that generates a set of codes equal to the total triplets number.
 \subsection{Selection}
-The first operator of the genetic algorithm is the selection [].
+The first operator of the genetic algorithm is the selection.
 The main objective of the selection is to choose the part of the current  population to be a candidate for the different genetic operators in order to breed the next generation population.
-Many selection techniques have been proposed in the literature [].
+Many selection techniques have been proposed in the literature~\cite{bli95}.
 In this approach the  process of natural selection is maintained.
@@
 \subsection{Crossover}
-The main operator of the GA is the crossover, allows to construct new solutions from the selected part of the population.
+The main operator of the GA is the crossover, allows to construct new solutions from the selected part of the population~\cite{osa14}.
 The selected solutions are ranked by fitness and crossover two by two from high fitness to low.
@@
 \subsection{Mutation}
-The mutation operator changes the positions of two leaf nodes of the generated children (result of the crossover); this introduce the diversity in the search process, this diversification strategy allow the algorithm do conference to the global optimum.
+The mutation operator changes the positions of two leaf nodes of the generated children (result of the crossover)~\cite{muhlenbein1992genetic}; this introduce the diversity in the search process, this diversification strategy allow the algorithm do conference to the global optimum.
 The algorithm for this operator goes through the leaf nodes and change the position of two leaf nodes from a parent to another and selects the ones to change according to a fixed mutation rate (see fig.1).
@@
 \section{Experiments and Comparison}
-
-The effectiveness of the approach has been evaluated with different real genomic biological data, these genomes were downloaded from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$ \cite{pruitt2009ncbi}.
-We focused on the sequences alone, ignoring any header and any other exogenous information.
-In table 3, the different data sets are described with the size  of each of them in megabytes (MB) and the references on the biological data bank.
+The approach has been evaluated with different real genomic biological data.
+Different genomes size have been used for the evaluation, from small genome to human chromosome in order to evaluate the efficiency of the approach.The datasets were downloaded as FASTA text file from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$ \cite{pruitt2009ncbi}.
+The used genomes are described in table 1, the size are given in Megabyte and the reference on the NCBI database.
 
@@
 Genome 15&78.19 &50.60&35.28 \\\hline
-Genome 16& & & \\\hline
+Genome 16& 168.98& & \\\hline
 Genome 17& & & \\\hline
@@
 \end{table}
+Table 2 presents thee results obtained by the proposed approach and classical Huffman code.
+The results are presented with the total number of switches and the improvement rate.
+The results shows that the proposed approach optimise the power consumption of the whole genome by reducing the total number of inter- ad intra-switches.
+In the best case the proposed approach improves power consumption over classical Huffman code by $x$, in the worst case by $x$, and on an average by $x$.
+The proposed approach optimise the total number of switches by swapping finding the best arrangement of nodes on the codewords tree with the best allocation of these codewords to the different frequencies (triplet).
+The approach continue swapping between the population individuals until a balance is found between inter-switches and intra-switches.
+
 \section{Conclusion}

### 2015-02-25 Switche Paper 1st approache/elsarticle-template-num.tex
exproments

@@
 Genome 15&78.19 &50.60&35.28 \\\hline
-Genome 16& 168.98& & \\\hline
-Genome 17& & & \\\hline
+Genome 16& 168.98& 102.13&39.56 \\\hline
+Genome 17&217.68 &130.93 & 39.85 \\\hline
 Genome 18& & & \\\hline

### 2015-02-25 Switche Paper 1st approache/elsarticle-template-num.tex
abstract

@@
 
-\title{Reducing Power Consumption in Huffman Coding}
+\title{Switching Optimisation in Huffman Code for Power Efficient   Data Transmission }
 
@@
 \begin{abstract}
-%% Text of abstract
-Recently the power consumption identified as one of the most pressing challenges of data transmission.
+
+Reliability of low powered devices is highly dependent on their power efficiency.
+In digital communication, a significant amount of power is dissipated in data transmission.
+Different technologies have been emerged to address the issues of power consumption.
+In CMOS technology, dynamic power accounts for 70\%-90\% of the total power dissipation and it depends on the representation of the data  and increases linearly with switching activities (transition from logic level High to Low and vice versa).
+Therefore, an efficient representation of data can minimise power consumption by reducing switching activities.
+In this paper, we have extended the Huffman code, a widely used data compression technique, by using genetic algorithm to reduce switching activities in the transmitted message.
+%In Recently the power consumption identified as one of the most pressing challenges of data transmission.
 Though a considerable reduction of size of data is obtained by Huffman code and several methods have been proposed to improve the data compression rate.
@@
 In this paper, we propose a new approach to reduce the power consumption, by applying genetic algorithm for minimising the total number of switches, either inter- or intra-switch.
-The approach starts it operation by generating a set of trees considered as initial population for the genetic algorithm, each one of these trees represent a set of codewords (solution), after that the genetic operators such as selection, crossover and mutation will be applied to the initial population in order to evolute the quality of the solutions.
-The amount of power consumption is proportional to the total number of switches on the whole sequence.
-The performance of the approach is evaluated by applying it to compress some standard biological datasets.
-The experiments yield that the proposed approach improves the power consumption rate considerably comparing with classic Huffman code.
+The main objective of the proposed approach is to minimise the switching activities in the codeword of each symbol as well as the switching activities between the symbols.
+The approach starts its operation by generating an initial population, a set of Huffman trees, for all the input symbols.
+Afterwards, the genetic operators such as selection, crossover and mutation are applied to the initial population to improve the quality of the solutions.
+%The amount of power consumption is proportional to the total number of switches on the whole sequence.
+The performance of the approach is evaluated by applying it to a set of real biological datasets.
+The experiments yield that the proposed approach reduces the switching activity by $45.47\%$ in the best case, by $36.33\%$ in the average case and by $16.42\%$ in the worst case.
 \end{abstract}
@@
 \section{Background}
-\subsection{Huffman Coding}
-\subsection{Power consumption}
+\subsection{Effect of Switching in Power Consumption}
+\subsection{Huffman Code and Its Relationship with Switching Activity}
+%\subsubsection{Relationship between switching and Huffman Code}
+
 \subsection{Issues in Biological data transmission}

### 2015-02-26 Switche Paper 1st approache/elsarticle-template-num.tex
good

@@
 Genome 17&217.68 &130.93 & 39.85 \\\hline
-Genome 18& & & \\\hline
+Genome 18& 243.70& 149.80&38.53 \\\hline
 %\bottomrule

### 2015-02-26 Switche Paper 1st approache/elsarticle-template-num.tex
some work

@@
 \usepackage{multirow}
+\usepackage{amsmath}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
+\usepackage{algcompatible}
 %% The amsthm package provides extended theorem environments
@@
 \subsection{Effect of Switching in Power Consumption}
+CMOS is the most widely used technology implemented in VLSI chips because of their power efficiency.
+Power dissipation in CMOS circuits has three different components: dynamic, static, and leakage \cite{Weste88}.
+\begin{equation*}
+P_{avg} = P_{dynamic}+P_{static}+P_{leakge} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\end{equation*}
+\begin{equation}
+~~~~~~~~~~~~= 0.5 \times C_{L} \times V_{dd}^{2}\times E(sw)\times f_{clk} + I_{sc} \times V_{dd}+I_{leakage} \times V_{dd}
+ \end{equation}
+ where\\
+  $C_{L}$ is the load capacitance, \\
+  $V_{dd}$ is power supply,\\
+  $E(sw)$ is average transition (switching) number per clock cycle ,\\
+  $f_{clk}$ is the clock frequency,\\
+  $ I_{sc}$ is the short circuit current, and\\
+  $ I_{leakage}$ is the leakage current.\\
+Out of the three components, the dynamic power dissipation is the dominant and it counts for 70\%-90\% of the total power consumption\cite{pedram1996}.
+Therefore, optimisation of dynamic power consumption is considered in this paper.
+In CMOS circuit, dynamic power consumption arises when the load capacitance ($C_{L}$) is charged to address a transition from low to the high voltage level.
+The parameters $C_{L}$, $V_{dd}$, and $f_{clk}$ in dynamic power dissipation are primarily determined by the circuit layout and the fabrication technology.
+However, amount of switching, $E(sw)$ completely depends on the digital representation of the data.
+As the dynamic power dissipation is proportional  to the average number of switching, thus a reduction in the total switching number will eventually results in the reduction of the dynamic power consumption.
+Therefore, in this paper, we focus on reducing total amount of switching in Huffman code to improve power efficiency of digital data processing.
+%In this paper, by switching we mean a transition from `0' to `1' or `1' to `0' in a binary sequence. 
 \subsection{Huffman Code and Its Relationship with Switching Activity}
 %\subsubsection{Relationship between switching and Huffman Code}
+In computer science and information theory, Huffman code is an entropy encoding algorithm used for lossless data compression.
+The classical Huffman code requires to pass the input data two times to complete the encoding operation.
+In the first pass, it reads the whole stream to determine the occurrence frequencies of distinct symbols.
+After that, symbols along with their frequencies are used to generate a binary tree known as Huffman tree.
+The process of Huffman tree generation is shown in algorithm 1 \cite{Cormen2001}.
+
+\begin{algorithm}[!thpb]
+\label{alg1}
+\caption{Huffman(C)}
+\begin{algorithmic}[1]
+\State $n \leftarrow |C|$
+\State $Q \leftarrow C$
+\FOR {$i = 1~to~n-1$}
+\State $allocate~a~new~node~z$
+\State $left[z]$ $\leftarrow$ $x$ $\leftarrow$ $EXTRACT\_MIN (Q)$
+\State $right[z]$ $\leftarrow$ $y$ $\leftarrow$ $EXTRACT\_MIN (Q)$
+\State $f[z]$ $\leftarrow$ $f[x] + f[y]$
+\State $INSERT (Q~,~z)$
+\ENDFOR
+\State \textbf{$retur$n} $EXTRACT-MIN (Q)$
+\end{algorithmic}
+\end{algorithm}
+In the algorithm, C is the set of n distinct symbols, and each symbol $ c\in C$ has a frequency denoted as f[c].
+The algorithm starts its operation with a set of $|C|$  leaf nodes where each node corresponds to a distinct symbol.
+After that, a sequence of $|C|-1$ merging operation is performed to obtain the final tree.
+The merging is done by extracting two least frequent symbols from the minimum priority queue, $Q$, and creating and inserting a new node (parent) to the queue for that two symbols.
+The frequency of the new  node is calculated as the sum of the frequency of its child nodes.
+The resultant tree ensures the optimal encoding of symbols to obtain maximal compression performance.
+The tree is traversed from the root to the leaf nodes to obtain the unique codeword (binary string) for different symbols.
+Once the codewords are obtained, in the second pass, the Huffman algorithm encodes the symbols of the input message with the codewords, thus reduce the size of the whole message.
+For a set of symbols more than one Huffman tree is possible, i.e., optimal solution can be obtained from different structure of the tree.
+If the structure of the tree is changed, the codewords for the symbols will also change.
+The switching activity depends on the structure of the codewords.
+For example, if a symbol is assigned a codewrod `000' then there is no switching, on the other hand, if the codeword `010' is assigned to a symbol the transmission of this symbol requires 2 switching activity.
 

### 2015-02-27 Switche Paper 1st approache/elsarticle-template-num.tex
some work

@@
  where\\
+  $P_{avg}$ is the average power dissipation
   $C_{L}$ is the load capacitance, \\
@@
 As the dynamic power dissipation is proportional  to the average number of switching, thus a reduction in the total switching number will eventually results in the reduction of the dynamic power consumption.
-Therefore, in this paper, we focus on reducing total amount of switching in Huffman code to improve power efficiency of digital data processing.
+Therefore, we focus on reducing total amount of switching in Huffman code to improve power efficiency of digital data processing.
 %In this paper, by switching we mean a transition from `0' to `1' or `1' to `0' in a binary sequence. 
@@
 \ENDFOR
-\State \textbf{$retur$n} $EXTRACT-MIN (Q)$
+\State \textbf{$retur$n} $EXTRACT\_MIN (Q)$
 \end{algorithmic}
@@
 The merging is done by extracting two least frequent symbols from the minimum priority queue, $Q$, and creating and inserting a new node (parent) to the queue for that two symbols.
+These two symbols are considered as the left and right child of their parent node respectively.
 The frequency of the new  node is calculated as the sum of the frequency of its child nodes.
 The resultant tree ensures the optimal encoding of symbols to obtain maximal compression performance.
-The tree is traversed from the root to the leaf nodes to obtain the unique codeword (binary string) for different symbols.
+%The tree is traversed from the root to the leaf nodes to obtain the unique codeword (binary string) for different symbols.
+To form a codeword for a symbol, the tree is traversed from the  root to the leaf node representing the symbol.
+In the traversal process, any move made towards the left direction is replaced by `0' and any move towards the right direction is replaced by `1'.
+As a result codeword for each symbol consist of a sequence of 0's and/or 1's.
 Once the codewords are obtained, in the second pass, the Huffman algorithm encodes the symbols of the input message with the codewords, thus reduce the size of the whole message.
 For a set of symbols more than one Huffman tree is possible, i.e., optimal solution can be obtained from different structure of the tree.
-If the structure of the tree is changed, the codewords for the symbols will also change.
-The switching activity depends on the structure of the codewords.
-For example, if a symbol is assigned a codewrod `000' then there is no switching, on the other hand, if the codeword `010' is assigned to a symbol the transmission of this symbol requires 2 switching activity.
+As the codeword of a symbol depend on its position in the tree, therefore changing the structure of the tree will change the codeword for the symbol.
+A codeword can contain zero or more switching activity within itself refereed to as intra-switch.
+For example, if a symbol `A' is assigned a codewrod `000' then there is no intra-switch, on the other hand, if the codeword `101' is assigned to a symbol `B` then their exist two intra-switches.
+When the codewords of different symbols are concatenated together during transmission they form switching based on the head and tail bit of the codewords.
+For example, if we want to transmit `AB' then according to the above codewords we will transmit `00\textbf{01}01' which will result in an inter-switch because the tail bit (0) of `A' and the head bit (1) of `B' are different.
+That means, in this case, we have three total switches--two intra-switches and one inter-switch.
+Now if `B' is assigned the codeword `010', the new transmitted string is `00\textbf{00}10', then we still have two intra-switches for the codeword of `B' but the inter-switch no more exists.
+So, changing tree structure, i.e., codewords, will change the total number of switching.
+Hence, the aim of this paper is to find an optimal Huffman tree that will minimise the total number of switching by making a balance between intra- and inter-switches.
 
 \subsection{Issues in Biological data transmission}
-The size of biological data base increase with an expanding rate and it doesn't stop for increasing.
-In the last decade the use of biological data history increase which evolve a high request to data from this high volume biological data base~\cite{Doug08}.
-The exponential growth of these databases become a big problem to all biological data processing methods~\cite{Doug08}.
-Data compression methods is the most used methods to evolve the reduce the cost of treatment of high volume data bases.
+The size of biological databases are continuously increasing.
+In the last decade the access to these databases has increased significantly.
+The exponential growth of these databases pose a big problem to all biological data processing methods~\cite{Doug08}.
+Data compression methods are widely used to reduce the overheads of treating, e.g., transmitting, the high volume of data.
 The main objective of data compression methods is minimising the number of bits in the data representation.
 Authors in~\cite{bra09} proposed a new approach to genomic data compression based in suffix and common substring and code the difference with Huffman code.
-In~\cite{chr09}, authors propose a general scheme for coding only the difference between the target genome and the referential one, the coding method used is Huffman.
-Recent work on data compression for biological data have been proposed to deal with transmission of genomic data as an email attachment~\cite{wan11}.
-Cost of data transmission is based on two point, firstly the size of the data which has been improved considerably in the recent year with the improvement of Huffman code.
+In~\cite{chr09}, authors propose a general scheme based on Huffman code for coding only the difference between the target genome and the referential one.
+Recently, a method has been proposed to deal with the transmission of genomic data as an email attachment~\cite{wan11}.
+All the methods used for biological data compression aims only at reducing the size of the data.
+However, due to the huge size of the input data, the compressed data contains a huge number of switching in them which has a big impact on power consumption.
+As no consideration is paid to the reduction of switching, hence, the compression process may be size efficient but not power efficient.
+Therefore, it is believed that a more efficient compression of biological data can be obtained by optimising the size of the data as well as the total number of switching in the transmitted data.
+%Cost of data transmission is based on two point, firstly the size of the data which has been improved considerably in the recent year with the improvement of Huffman code.
 Secondly, is the number of switches on the generated codes.
-The power consumption increase linear with the number of switches.
-\section{GA-SO : Genetic algorithm for Switches Optimising}
-Genetic algorithm (GA) is one the of the most popular bio-inspired meta-heuristic algorithm inspired from the natural evolution of species~\cite{gen1}.
+%The power consumption increase linear with the number of switches.
+\section{The proposed approach for Switching Optimisation}
+The main objective of the approach is to minimise the total number of switching in the representation of data produced by the Huffman algorithm.
+To do so, it is required to minimise both intra- and inter-switches among the codewords.
+The total number of intra-switch depends on the codewords themselves and the frequency of the symbols.
+As a result, for  a given set of codewords an optimal number of intra-switches can be obtained by assigning the most frequent symbol with the codewords with minimum number of switching.
+However, it will not ensure the optimal number of inter-switches.
+Because, inter-switches not only depend on the codewords of the symbols but also the association between the symbols.
+By association, we mean how many times a symbol occurs after another symbol in the whole message, i.e., all possible pairing combination among the symbols.
+As the number of distinct symbols increases in the message the number of combination increases.
+So improving total number of inter-switching is a combinatorial problem.
+
+Genetic algorithm (GA) has widely been applied to solve a range of combinatorial problem in complex VLSI design~\cite{chan1991macro,bright1996genetic,cohoon1987genetic}.
+For this reason, the GA is identified as a potential solution to the above mentioned problem.
+GA is one the of the most popular bio-inspired meta-heuristic algorithm inspired by the natural evolution of species~\cite{gen1}.
 It is a population based algorithm starts with the generation of a random initial population.
@@
 The GA optimisation process uses a set of natural genetic operators such as selection, crossover and mutation to converge to the optimal solution.
-\subsection{Preparing data and population generation}
-A genome is an expansion of DNA sequence which is a set of nucleotides that encodes a protein.These nucleotide are bounded together and each order define a specific protein.
-The transformation of DNA sequence to protein  is made by the cellular machinery, each three nucleotides are interpreted to a specific amino acid this three nucleotide are called triplets~\cite{Harvey00}.
-Huffman algorithm read the whole message to compute frequencies, the proposed algorithm read the whole genome and cut it into triplet to generate the frequencies of the triplet and by the way to generate the adjacent matrix which represents the frequencies precedence between triplet.
-The initial population is generated randomly, each solution on the population represents a tree that generates a set of codes equal to the total triplets number.
-\subsection{Selection}
+\subsection{ Data preparation and population generation}
+A genome is an expansion of DNA sequence which is a set of nucleotides that encodes a protein.
+These nucleotides are bounded together and each order define a specific protein.
+Three nucleotides form a triplet and interpreted as a specific amino acid ~\cite{Harvey00}.
+For this reason, the whole sequence is divided into a set of triplets.
+As each DNA sequence contains a combination of four nucleobases\textemdash guanine (G), adenine (A), thymine (T), and cytosine (C), therefore we will have $4^3=64$ possible triplets.
+As mentioned earlier that the classical Huffman code requires reading the whole sequence prior to encoding.
+So, in this case, the whole DNA sequence is read considering different triplets as distinct symbols.
+Frequencies for each of the triplets are calculated and  the adjacency matrix (a symmetric 2D matrix) is also created which represents how many times a triplet occurs after each of the other triplets.
+After that, a random set of Huffman trees are generated for the input symbols (triplets) which are considered as the initial population for the GA.
+ \subsection{Genetic operations}
+\subsubsection{Selection}
 The first operator of the genetic algorithm is the selection.
@@
 After that, an unbiased random selection of \textit{$rand$}~individuals (solutions) from the population is maid.
-\subsection{Crossover}
+\subsubsection{Crossover}
 The main operator of the GA is the crossover, allows to construct new solutions from the selected part of the population~\cite{osa14}.
@@
 The crossover operation will create two new trees (solutions), the first child (second) contain the nodes that are not children of the \textit{$node1$} (\textit{$node2$}) and we replace the children of \textit{$node1$} (\textit{$node2$}) by the children of \textit{$node2$} (\textit{$node1$}) (see fig.1).
-\subsection{Mutation}
+\subsubsection{Mutation}
 The mutation operator changes the positions of two leaf nodes of the generated children (result of the crossover)~\cite{muhlenbein1992genetic}; this introduce the diversity in the search process, this diversification strategy allow the algorithm do conference to the global optimum.

### 2015-02-27 Switche Paper 1st approache/elsarticle-template-num.tex
conclusion finished

@@
 The results are presented with the total number of switches and the improvement rate.
-The results shows that the proposed approach optimise the power consumption of the whole genome by reducing the total number of inter- ad intra-switches.
+The results shows that the proposed approach optimise the power consumption of the whole genome by reducing the total number of inter- and intra-switches.
 In the best case the proposed approach improves power consumption over classical Huffman code by $x$, in the worst case by $x$, and on an average by $x$.
@@
 \section{Conclusion}
-In this paper we described how the genetic algorithm can be used to improve the power consumption in biological data transmission.
-The advantage of the proposed approach is that it minimise considerably the number of switches with affect directly the power consumption for data transmission.
-In this paper, we identified genetic
-algorithm as a potential method to optimise the total number of inter- and intra-switches.
-The Genetic algorithm start by generating a set of feasible solutions (trees), each one contain a set of codewords.
-After that, the approach uses the natural genetic operators to improve the quality if the solutions by generating new solution.
-the evolution of the population is controlled by the number of switches both inter- and intra-switches.
-The proposed approach is applied to biological data sets with different sizes from small genome to a human chromosome.
-The approach has been compared with the classic Huffman code.
-The results show that
-the proposed approach improves the power consumption rate considerably.
-The experiment shows that the proposed approach improves Huffman code in the best case with $best$,  $average$ in the average case, and $worst$ case.
-For the future we hope to improve the allocation of codewords to different frequencies in orderer to improve the total number of switches.
+In this paper, we showed how switching activities affect the power consumption in digital communication.
+After that, a relationship between the Huffman code and the switching activities is shown.
+Genetic
+algorithm is identified as a potential method to optimise the total number of  switching: inter- and intra-switching in Huffman code.
+Subsequently, an approach is proposed to show how the genetic algorithm can be used to reduce the power consumption in biological data transmission by reducing total number of switching in the  transmission.
+The proposed approach starts its operation by generating a set of feasible solutions (Huffman trees), each one contains a set of codewords for the input symbols.
+After that, the approach uses a set of natural genetic operators to improve the quality of the solutions by generating new solutions.
+The evolution of the population is controlled by the total number of switching.
+The advantage of this approach is that it minimises the total number of switching considerably, thus increases the power efficiency data transmission.
+The effectiveness of the proposed approach is evaluated by applying it to several biological data sets with different sizes varied from small genome to a human chromosome.
+The performance of the approach has been compared with the performance of the classical Huffman code.
+The results show that the proposed approach reduces the total number of switching significantly to improve the power efficiency of biological data transmission.
+%The experiment shows that the proposed approach improves Huffman code in the best case with $best$,  $average$ in the average case, and $worst$ case.
+In the future, we hope to improve the allocation method of codewords to different symbols to reduce further the total number of switching.
 

### 2015-02-27 Switche Paper 1st approache/elsarticle-template-num.tex
objectif

@@
 A codeword can contain zero or more switching activity within itself refereed to as intra-switch.
-For example, if a symbol `A' is assigned a codewrod `000' then there is no intra-switch, on the other hand, if the codeword `101' is assigned to a symbol `B` then their exist two intra-switches.
+For example, if a symbol `A' is assigned a codeword `000' then there is no intra-switch, on the other hand, if the codeword `101' is assigned to a symbol `B` then their exist two intra-switches.
 When the codewords of different symbols are concatenated together during transmission they form switching based on the head and tail bit of the codewords.
@@
 So, in this case, the whole DNA sequence is read considering different triplets as distinct symbols.
-Frequencies for each of the triplets are calculated and  the adjacency matrix (a symmetric 2D matrix) is also created which represents how many times a triplet occurs after each of the other triplets.
+Frequencies for each of the triplets are calculated and  the adjacency matrix (a square matrix) is also created which represents how many times a triplet occurs after each of the other triplets.
 After that, a random set of Huffman trees are generated for the input symbols (triplets) which are considered as the initial population for the GA.
+\subsection{Objective function}
+
+The main objective of the proposed approach is to generate a set of codewords that contain the minimum number of switches in order to minimise the power consumption.
+The objective function of switching optimisation algorithm can be formulated as follow :
+
+\textbf{Definition:} Let $C=\left\{C_{1},C_{2}...C_{n}\right\}$ be a set of codewords, let $F=\left\{F_{1},F_{2}...F_{n}\right\}$ be a set of frequencies of codes in the sequence, and let $M(n,n)$ be a square matrix represents the frequencies of the adjacency between codes.
+\\
+The Objective Function is to:
+
+\begin{equation}
+Minimise \sum_{i=1}^{n} (S(C_{i}) \times F_{i})~+~\sum_{i=1}^{n}\sum_{j=1}^{n} \mu(C_{i},C_{j}) \times M[i][j]  
+\end{equation}
+where\\
+$\mu(C_{i},C_{j})=1$ if the head of the codeword $C_{i}$ and tail bit of the codeword $C_{j}$ are different.\\
+$\mu(C_{i},C_{j})=0$ if the head of the codeword $C_{i}$ and tail bit of the codeword $C_{j}$ are equal.
+
 \subsection{Genetic operations}

### 2015-02-27 Switche Paper 1st approache/elsarticle-template-num.tex
up

@@
 The GA optimisation process uses a set of natural genetic operators such as selection, crossover and mutation to converge to the optimal solution.
-\subsection{ Data preparation and population generation}
-A genome is an expansion of DNA sequence which is a set of nucleotides that encodes a protein.
-These nucleotides are bounded together and each order define a specific protein.
-Three nucleotides form a triplet and interpreted as a specific amino acid ~\cite{Harvey00}.
-For this reason, the whole sequence is divided into a set of triplets.
-As each DNA sequence contains a combination of four nucleobases\textemdash guanine (G), adenine (A), thymine (T), and cytosine (C), therefore we will have $4^3=64$ possible triplets.
-As mentioned earlier that the classical Huffman code requires reading the whole sequence prior to encoding.
-So, in this case, the whole DNA sequence is read considering different triplets as distinct symbols.
-Frequencies for each of the triplets are calculated and  the adjacency matrix (a square matrix) is also created which represents how many times a triplet occurs after each of the other triplets.
-After that, a random set of Huffman trees are generated for the input symbols (triplets) which are considered as the initial population for the GA.
-\subsection{Objective function}
-
-The main objective of the proposed approach is to generate a set of codewords that contain the minimum number of switches in order to minimise the power consumption.
-The objective function of switching optimisation algorithm can be formulated as follow :
-
-\textbf{Definition:} Let $C=\left\{C_{1},C_{2}...C_{n}\right\}$ be a set of codewords, let $F=\left\{F_{1},F_{2}...F_{n}\right\}$ be a set of frequencies of codes in the sequence, and let $M(n,n)$ be a square matrix represents the frequencies of the adjacency between codes.
-\\
-The Objective Function is to:
-
-\begin{equation}
-Minimise \sum_{i=1}^{n} (S(C_{i}) \times F_{i})~+~\sum_{i=1}^{n}\sum_{j=1}^{n} \mu(C_{i},C_{j}) \times M[i][j]  
-\end{equation}
-where\\
-$\mu(C_{i},C_{j})=1$ if the head of the codeword $C_{i}$ and tail bit of the codeword $C_{j}$ are different.\\
-$\mu(C_{i},C_{j})=0$ if the head of the codeword $C_{i}$ and tail bit of the codeword $C_{j}$ are equal.
-
-\subsection{Genetic operations}
-\subsubsection{Selection}
-The first operator of the genetic algorithm is the selection.
-The main objective of the selection is to choose the part of the current  population to be a candidate for the different genetic operators in order to breed the next generation population.
-Many selection techniques have been proposed in the literature~\cite{bli95}.
-In this approach the  process of natural selection is maintained.
-First we generate a random pair numbers \textit{$rand$} between 2 and the population size, this number represent how many parents will be processed.
-After that, an unbiased random selection of \textit{$rand$}~individuals (solutions) from the population is maid.
-\subsubsection{Crossover}
-The main operator of the GA is the crossover, allows to construct new solutions from the selected part of the population~\cite{osa14}.
-The selected solutions are ranked by fitness and crossover two by two from high fitness to low.
-The main objective of the crossover is to benefits from the two good solutions in order to generate a better solution.
-An internal node for each tree (solution) is selected (\textit{$node1$},\textit{$node2$}), these two nodes must have the same number of leaf nodes (contain the same number of codes).
-The crossover operation will create two new trees (solutions), the first child (second) contain the nodes that are not children of the \textit{$node1$} (\textit{$node2$}) and we replace the children of \textit{$node1$} (\textit{$node2$}) by the children of \textit{$node2$} (\textit{$node1$}) (see fig.1).
-\subsubsection{Mutation}
-The mutation operator changes the positions of two leaf nodes of the generated children (result of the crossover)~\cite{muhlenbein1992genetic}; this introduce the diversity in the search process, this diversification strategy allow the algorithm do conference to the global optimum.
-The algorithm for this operator goes through the leaf nodes and change the position of two leaf nodes from a parent to another and selects the ones to change according to a fixed mutation rate (see fig.1).
-\subsection{Population update}
-The crossover operation aims to generate new solutions from the current solution to built the second generation of the population.
-Furthermore, the mutation provide the diversity on the search space solution by changing the position of  nodes on the same tree.
-After these two operations, the next step of the genetic algorithm is two to breed the new population (see fig.2).
-Firstly the new solutions (children) are added to the current population, after that the population is ranked by fitness.
-The algorithm remove the worst solutions until the initial size of the population is achieved.
-The algorithm genetic repeat these operators until the stopped criteria is achieved, in this algorithm the stopped criteria is when the objective function (number of switches) stop decreasing.
+The whole process is shown in algorithm 2.
 \begin{algorithm}[!btph]
@@
 \end{algorithm}
+\subsection{ Data preparation and population generation}
+A genome is an expansion of DNA sequence which is a set of nucleotides that encodes a protein.
+These nucleotides are bounded together and each order define a specific protein.
+Three nucleotides form a triplet and interpreted as a specific amino acid ~\cite{Harvey00}.
+For this reason, the whole sequence is divided into a set of triplets.
+As each DNA sequence contains a combination of four nucleobases\textemdash guanine (G), adenine (A), thymine (T), and cytosine (C), therefore we will have $4^3=64$ possible triplets.
+As mentioned earlier that the classical Huffman code requires reading the whole sequence prior to encoding.
+So, in this case, the whole DNA sequence is read considering different triplets as distinct symbols.
+Frequencies for each of the triplets are calculated and  the adjacency matrix (a square matrix) is also created which represents how many times a triplet occurs after each of the other triplets.
+After that, a random set of Huffman trees are generated for the input symbols (triplets) which are considered as the initial population for the GA.
+\subsection{Objective function}
+
+The main objective of the proposed approach is to generate a set of codewords for the input symbols to minimise the overall amount of switching.
+The objective function of the switching optimisation algorithm can be formulated as follow :
+
+\textbf{Definition:} Let $F=\left\{F_{1},F_{2},...,F_{n}\right\}$ and $C=\left\{C_{1},C_{2},...,C_{n}\right\}$ be the set of frequencies and codewords for the input symbols $S=\left\{S_{1},S_{2},...,S_{n}\right\}$ respectively.
+And $M(n,n)$ be the adjacency matrix where each entry $M[i][j]$ represents how many times the input symbol $S_j$ appears after the symbol $S_i$ in the whole sequence.
+\\
+The Objective Function is to:
+
+\begin{equation}
+Minimise~\Big( \sum_{i=1}^{n}~(~Sw(C_{i}) \times F_{i}~)~+~\sum_{i=1}^{n}\sum_{j=1}^{n}~(~\mu(C_{i},C_{j}) \times M[i][j]~)~\Big)  
+\end{equation}
+where,\\\\
+$Sw(C_{i})$ is the number of intra-switches in the codewords $C_{i}$\\
+$\mu(C_{i},C_{j})=1$ if the head (starting) bit of the codeword $C_{j}$ and the tail (ending) bit of the codeword $C_{i}$ are different.\\
+$\mu(C_{i},C_{j})=0$ if the head bit of the codeword $C_{j}$ and the tail bit of the codeword $C_{i}$ are equal.
+
+\subsection{Genetic operations}
+\subsubsection{Selection}
+The first operator of the genetic algorithm is the selection.
+The main objective of the selection is to choose the part of the current  population to be a candidate for the different genetic operators in order to breed the next generation population.
+Many selection techniques have been proposed in the literature~\cite{bli95}.
+In this approach the  process of natural selection is maintained.
+At first, we generate a random even number \textit{$rand$} between 2 and the population size.
+This number represents how many parents will be processed.
+After that, an unbiased random selection of \textit{$rand$}~individuals (solutions) from the population is made.
+\subsubsection{Crossover}
+The main operator of the GA is the crossover, allows to construct new solutions from the selected part of the population~\cite{osa14}.
+The selected solutions are ranked by fitness and sorted in descending order.
+After that, at a time, a pair of solution is taken from the sorted population and then crossed to generate two new solutions.
+This process continues until all the pairs of solutions are crossed.
+The main objective of the crossover is to benefits from the two solutions  to generate better solutions.
+Two parent trees are crossed to find two new child trees in the following way:\\\\
+\textbf{Step 1: }Select an internal node (a sub-tree) from each parent tree with equal number of nodes (the dashed selection in Fig. 1(a) and (b)). \\
+\textbf{Step 2:} Put the selected sub-tree of the first tree in the place of the selected sub-tree of the second tree and vice versa (see Fig. 1(c) and (d)).\\
+
+However, in each of the trees some symbols are repeated and some are missed, but number of repeated and missed symbols are equal.
+This is because we replace a sub-tree by other sub-tree without any modification.
+As a result each child tree contains a part from its parent tree and a part from the other tree.
+If the remaining part from the parent tree and the newly added part has one or more  symbols in common then these symbols will be repeated in the tree, on the other hand, the uncommon symbols between the newly added sub-tree and  the replaced sub-tree will be missed.
+We solved this conflict by putting the missed symbols one by one in the place of the repeated symbol in the remaining part from the parent tree.
+That means, the newly added sub-tree is kept unchanged and all the replacements are done on the old part of the tree.
+
+\subsubsection{Mutation}
+The mutation operator changes the positions of two leaf nodes of the generated children (result of the crossover)~\cite{muhlenbein1992genetic}.
+It introduces the diversity in the search process, this diversification strategy allow the algorithm to converge to the optimal solution.
+The algorithm for this operator goes through the leaf nodes and change the positions of two leaf nodes from their current positions to another positions in the tree (see Fig.1(e) and (f)).
+The selection of the nodes to be mutated is done following a fixed mutation rate.
+
+\subsection{Population update}
+The crossover operation generates new solutions from the current solutions to build the second generation of the population.
+Furthermore, the mutation process provides the diversity in the search on the solution space by changing the position of the nodes in the same tree.
+After these two operations, the next step of the genetic algorithm is to breed the new population (see fig.2).
+Firstly, the new solutions (children) are added to the current population and ranked by fitness.
+The algorithm remove the worst solutions until the initial size of the population is achieved.
+The genetic algorithm  continuously repeats the selection, crossover, mutation, and population update operation until the stopping criteria is achieved.
+In the proposed approach the stopping criteria is when the objective function (number of switches) stop decreasing.
 \begin{figure}[tbph]
@@
 \begin{center}
-\includegraphics[width=350pt,height=170pt]{Images/Drawing3.jpg}
+\includegraphics[scale=0.7]{Images/Drawing_1.jpg}
 \caption{Population update for genetic algorithm}
@@
 \label{table4}
-\caption{Comparison of performance among classical Huffman code, CCA, and OCCA without penalty}
+\caption{Comparison of the total number of switches (in millions) between the Huffman code and the proposed approach}
 %\begin{center}
@@
 \hline
- & Huffman Algorithm & P \\\hline
-\\\hline
+ Datasets & \begin{tabular}{@{}c@{}}Switches in the\\ Huffman Code\end{tabular} & \begin{tabular}{@{}c@{}}Switches in the\\ proposed approach\end{tabular}& Improvement (\%) \\\hline
 Genome 1& 18.16 & 10.05 & 44.65 \\\hline

### 2015-02-28 Switche Paper 1st approache/elsarticle-template-num.tex
modification completed

@@
 The performance of the approach is evaluated by applying it to a set of real biological datasets.
-The experiments yield that the proposed approach reduces the switching activity by $45.47\%$ in the best case, by $36.33\%$ in the average case and by $16.42\%$ in the worst case.
+The experiments yield that the proposed approach reduces the switching activity by $45.47\%$ in the best case, by $36.45\%$ in the average case, and by $16.42\%$ in the worst case.
 \end{abstract}
@@
 \caption{Switches optimising Huffman codes}
-\label{alg1}
+\label{alg2}
 \begin{algorithmic}[1]
 \REQUIRE Textual representation of a Genome
-\ENSURE Low switches Huffman codes
-\STATE Generate triplet frequencies and adjacent matrix 
+\ENSURE Huffman codes with optimal number of switching
+\STATE Generate triplet frequencies and adjacency matrix 
 \STATE Generate the initial  population of trees
@@
 \STATE Rank by fitness
-\STATE Remove worst solutions until population limit
-\UNTIL{The switches number stop decreasing}
+\STATE Remove worst solutions until population limit reached
+\UNTIL{the switching number stop decreasing}
 %\algstore{myalg}
@@
 
-However, in each of the trees some symbols are repeated and some are missed, but number of repeated and missed symbols are equal.
-This is because we replace a sub-tree by other sub-tree without any modification.
-As a result each child tree contains a part from its parent tree and a part from the other tree.
+However, in each of the trees, some symbols are repeated and some are missed, but number of repeated and missed symbols are equal.
+This is because, we replace a sub-tree by other sub-tree without any modification.
+As a result each new (child) tree contains a part from its parent tree and a part from the other tree.
 If the remaining part from the parent tree and the newly added part has one or more  symbols in common then these symbols will be repeated in the tree, on the other hand, the uncommon symbols between the newly added sub-tree and  the replaced sub-tree will be missed.
@@
 It introduces the diversity in the search process, this diversification strategy allow the algorithm to converge to the optimal solution.
-The algorithm for this operator goes through the leaf nodes and change the positions of two leaf nodes from their current positions to another positions in the tree (see Fig.1(e) and (f)).
+The algorithm for this operator goes through the leaf nodes and change the positions of two leaf nodes from their current positions to another positions in the tree (see Fig.2(a) and (b)).
 The selection of the nodes to be mutated is done following a fixed mutation rate.
@@
 Furthermore, the mutation process provides the diversity in the search on the solution space by changing the position of the nodes in the same tree.
-After these two operations, the next step of the genetic algorithm is to breed the new population (see fig.2).
+After these two operations, the next step of the genetic algorithm is to breed the new population (see Fig.3).
 Firstly, the new solutions (children) are added to the current population and ranked by fitness.
@@
 \begin{center}
-\includegraphics[width=400pt,height=545pt]{Images/Drawing1-1.jpg}
-\caption{The Crossover operator}
+\includegraphics[width=380pt,height=500pt]{Images/figure1.jpg}
+\caption{The Crossover operation}
 \end{center}
@@
 \end{figure}
+
+\begin{figure}[tbph]
+\begin{center}
+\includegraphics[scale=0.4]{Images/figure2.jpg}
+\caption{The Mutation operation}
+\end{center}
+\label{Fig2}
+\end{figure}
+
 \begin{figure}[tbph]
@@
 \end{center}
-\label{Fig2}
+\label{Fig3}
 \end{figure}
@@
 \section{Experiments and Comparison}
-The approach has been evaluated with different real genomic biological data.
-Different genomes size have been used for the evaluation, from small genome to human chromosome in order to evaluate the efficiency of the approach.The datasets were downloaded as FASTA text file from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$ \cite{pruitt2009ncbi}.
-The used genomes are described in table 1, the size are given in Megabyte and the reference on the NCBI database.
+The proposed approach is used to reduce the total number of switching activities during data transmission.
+The approach optimises the total number of switching by  finding  the best arrangement of nodes by rearranging their positions in the codewords tree with the best allocation of these codewords to the different frequencies (triplets).
+It continues swapping between the individual population  until a balance is found between inter-switching and intra-switching.
+The effectiveness of the approach has been evaluated by applying is to compress different real genomic biological data.
+Different genomes size have been used for the evaluation, from small genome to large human chromosome.
+The datasets were downloaded as FASTA text file from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$ \cite{pruitt2009ncbi}.
+The used genomes are described in table 1 with their reference in the NCBI database, the size of all the files are given in Megabytes (MBs).
 
@@
 \hline
- Datasets & \begin{tabular}{@{}c@{}}Switches in the\\ Huffman Code\end{tabular} & \begin{tabular}{@{}c@{}}Switches in the\\ proposed approach\end{tabular}& Improvement (\%) \\\hline
+ Datasets & \begin{tabular}{@{}c@{}}Switches in the Huffman\\  Code (in millions)\end{tabular} & \begin{tabular}{@{}c@{}}Switches in the proposed\\  approach (in millions)\end{tabular}& Improvement (\%) \\\hline
 Genome 1& 18.16 & 10.05 & 44.65 \\\hline
@@
 \end{table}
-Table 2 presents thee results obtained by the proposed approach and classical Huffman code.
-The results are presented with the total number of switches and the improvement rate.
-The results shows that the proposed approach optimise the power consumption of the whole genome by reducing the total number of inter- and intra-switches.
-In the best case the proposed approach improves power consumption over classical Huffman code by $x$, in the worst case by $x$, and on an average by $x$.
-The proposed approach optimise the total number of switches by swapping finding the best arrangement of nodes on the codewords tree with the best allocation of these codewords to the different frequencies (triplet).
-The approach continue swapping between the population individuals until a balance is found between inter-switches and intra-switches.
+In the experiments, we compare the performance of the classical Huffman code with the performance of the proposed method in terms of the total number of switching.
+Table 2 presents the results obtained by the proposed approach and the classical Huffman code.
+The results are presented as the total number of switching activities in both the approaches and the improvement rate.
+The improvement rate (reduction ratio) is calculated as:\\
+\begin{equation}
+Improvement~ Rate = (1-\frac{Switching~ in ~proposed~ approach}{Switching~ in ~ the ~Huffman ~code})\times 100
+\end{equation}
+ \\The results show that the proposed approach optimises the total number of switching  of the whole genome by reducing the total number of inter- and intra-switching.
+In the best case the proposed approach reduces the total number of switching over the classical Huffman code by $45.47\%$, in the worst case by $16.42\%$, and on an average by $36.45\%$.
 
